---
title: "Data Preparation"
format:
  html:
    toc: true
    toc-depth: 6
code-line-numbers: true
code-annotations: true
editor_options: 
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages
```{r}
pacman::p_load(tidyverse, haven)
```

### Import Raw p1_datast
```{r}
p1_data <- read_sav("data/tk_2020.sav")
names(p1_data) <- tolower(names(p1_data))
```

## Create Variables
### Recode PSX
```{r}
p1_data <- p1_data %>%
  mutate(
    across(c(esm12, esm19:esm22), ~ .x - 1) #<1>
  ) %>%
  mutate(
    esm_psx_sum = rowSums(across(c(esm12, esm19:esm22)), na.rm = FALSE) #<2>
  )
```

:::callout-note
I'm creating my own version of the Psychotic-like Experiences composite variable. The existing variables/indices seek to address the big floor effect. We actually have a decent way of addressing this according to Muthen et al.

We will create a regular 
:::

### Create Time Variable
```{r}
p1_data <- p1_data %>%
  mutate(
    datetime = as_datetime(date) + time 
  ) %>%
  group_by(id) %>%
  arrange(datetime, .by_group = TRUE) %>%
  mutate(
    time_hour = as.numeric(difftime(datetime, first(datetime), units = "hours"))
  ) %>%
  mutate(
    time_day = as.numeric(difftime(datetime, first(datetime), units = "days"))
  ) %>%
  ungroup()
```

### Drop Missing Time
```{r}
org_count <- p1_data %>%
  nrow()
org_count
clean_count <- p1_data %>% 
  filter(!is.na(time_day)) %>%
  nrow()
clean_count

org_count - clean_count
```

:::callout-note
We only lost 36 responses, miniscule.
:::

```{r}
p1_data <- p1_data %>% 
  filter(!is.na(time_day))
```

## Descriptives
### What is N?
```{r}
n_distinct(p1_data$id)
```

### All Variables
```{r}
tidySEM::descriptives(p1_data) %>%
  select(name, n, missing, unique, mean, sd, min, max, range, skew, kurt) %>%
  mutate(across(where(is.numeric), ~round(.x, 2))) %>%
  DT::datatable()
```

### Codebook

code_data <- p1_data %>%
  mutate(across(esm01:esm30, as.factor))
  
```{r}
code_data <- p1_data %>%
  mutate(across(esm01:esm30, as.factor))
memisc::Write(memisc::codebook(code_data),
              file = "01_files/p1_data_codebook.txt")
```


## Visualize 

:::callout-note
Overall, there is a non-negligible floor effects in some variables. I will attempt to address some, but others we will have to see how the model handles skewed variables.
:::

### Level 2 Variables
```{r}
library(patchwork)
p1_data %>%
  ggplot(aes(zpos)) +
  geom_bar() +
  labs(x = "POS") +
  
p1_data %>%
  ggplot(aes(zneg)) +
  geom_bar() +
  labs(x = "NEG") +

p1_data %>%
  ggplot(aes(zdis)) +
  geom_histogram(binwidth = 0.1) +
  labs(x = "DIS")
```

### Composite Indices
:::callout-important
`Positive Affect` demonstrates pretty good distribution qualities. Can't say the same for any other composite variable. 
:::

```{r}
p1_data %>%
  ggplot(aes(esm_pa)) +
  geom_bar() +
  
p1_data %>%
  ggplot(aes(esm_na)) +
  geom_bar() +

p1_data %>%
  ggplot(aes(esm_neg3)) +
  geom_bar() +

p1_data %>%
  ggplot(aes(esm_dis)) +
  geom_bar() +

p1_data %>%
  ggplot(aes(esm_psx_sum)) +
  geom_bar()
```

### Items
```{r}
bar_pct <- function(data, var) {
  ggplot(data, aes({{ var }})) +
    geom_bar(aes(y = after_stat(count / sum(count) * 100))) +
    geom_text(aes(y = after_stat(count / sum(count) * 100),
                  label = after_stat(paste0(round(count / sum(count) * 100, 1), "%"))),
              stat = "count", vjust = -0.3) +
    labs(y = "Percent") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
}
```

:::callout-warning
This is a custom convenience function that makes visualization easier with less code. Created using Claude.ai.
:::

#### Positive Aff
```{r}
(bar_pct(p1_data, esm01) +
bar_pct(p1_data, esm05) +
bar_pct(p1_data, esm09)) +
  plot_layout(ncol = 2)
```

#### Negative Aff
```{r}
(bar_pct(p1_data, esm02) +
bar_pct(p1_data, esm03) +
bar_pct(p1_data, esm06)) +
  plot_layout(ncol = 2)
```

#### Negative Experiences
```{r}
(bar_pct(p1_data, esm11) +
bar_pct(p1_data, esm13) +
bar_pct(p1_data, esm15)) +
  plot_layout(ncol = 2)
```

#### Psychotic-like Exp.
```{r}
(bar_pct(p1_data, esm12) +
bar_pct(p1_data, esm19) +
bar_pct(p1_data, esm20) +
bar_pct(p1_data, esm21) +
bar_pct(p1_data, esm22)) +
  plot_layout(ncol = 2)
```

#### Disorganized Experiences
```{r}
(bar_pct(p1_data, esm04) +
bar_pct(p1_data, esm07) +
bar_pct(p1_data, esm10)) +
  plot_layout(ncol = 2)
```


## Separating Floor Effect
:::callout-important
Luckily, [Muthen et al.](https://www.statmodel.com/download/DSEMFloorEffects.pdf) actually came out with a pretty clever and theoretically meaningful way to address floor effects: a **hurdle modeling** approach.

Instead of dropping the floor effect (the lowest value possible), Muthen et al. recommends creating two variables from the original variable.

**Step 1**: Create a binary variable.  
Create a binary variable that collapses all **non-floor** scores as `1`. Thus, *conceptually* this variable represents whether a construct is meaingfully *occuring* or not.

BIN = 0, the construct is not meaningfully occuring.
BIN = 1, the construct is meaningfully occuring. 

We *do* loose information about the magnitude of how this construct is taking place, but that's where part 2 comes in.

**Step 2**: Create a continuous variable.  
In the second step, we code all floor effects as `NA` (i.e., missing) and retain non-floor effects as original.

Thus, the continous variable is represents what is taking place **AFTER** removed floor effects which drowned out the variance. 

Thus, in analytical models we should include **both** variables (only possible in SEMs) and allowed to correlate with one another. In doing so, we can understand if a distal variable is related to the **occurrence** of a construct *AND* also when it is occurring, the **magnitude** of that relationship.

For the truncated variable, we will use a tobit/censored specification. 
:::

### Neg-Aff
```{r}
#| fig-width: 12
#| fig-height: 5
p1_data <- p1_data %>%
  mutate(
    esm_na_bin = ifelse(esm_na == 1, 0, 1),
    esm_na_con = ifelse(esm_na == 1, NA, esm_na)
  )

bar_pct(p1_data, esm_na)

bar_pct(p1_data, esm_na_bin) +
bar_pct(p1_data, esm_na_con) +
  patchwork::plot_layout(widths = c(1, 2))
```


### Negative Exp.
```{r}
#| fig-width: 12
#| fig-height: 5
p1_data <- p1_data %>%
  mutate(
    esm_neg3_bin = ifelse(esm_neg3 == 1, 0, 1),
    esm_neg3_con = ifelse(esm_neg3 == 1, NA, esm_neg3)
  )

bar_pct(p1_data, esm_neg3)

bar_pct(p1_data, esm_neg3_bin) +
bar_pct(p1_data, esm_neg3_con) +
  patchwork::plot_layout(widths = c(1, 2))
```

### Disorganized Experiences
```{r}
#| fig-width: 12
#| fig-height: 5
p1_data <- p1_data %>%
  mutate(
    esm_dis_bin = ifelse(esm_dis == 1, 0, 1),
    esm_dis_con = ifelse(esm_dis == 1, NA, esm_dis)
  )

bar_pct(p1_data, esm_dis)

bar_pct(p1_data, esm_dis_bin) +
bar_pct(p1_data, esm_dis_con) +
  patchwork::plot_layout(widths = c(1, 2))
```

### Psychotic-like Exp.
```{r}
#| fig-width: 12
#| fig-height: 5
p1_data <- p1_data %>%
  mutate(
    esm_psx_bin = ifelse(esm_psx_sum == 0, 0, 1),
    esm_psx_con = ifelse(esm_psx_sum == 0, NA, esm_psx_sum)
  )

bar_pct(p1_data, esm_psx_sum)

bar_pct(p1_data, esm_psx_bin) +
bar_pct(p1_data, esm_psx_con) +
  patchwork::plot_layout(widths = c(1, 2))
```

```{r}
#| include: false

saveRDS(p1_data, "data/p1_data.Rds")
```