---
title: "Positive Affect"
format:
  html:
    toc: true
    toc-depth: 6
code-line-numbers: true
code-annotations: true
editor_options: 
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
```

```{r}
#| include: false
p2_data <- readRDS("data/p1_data.Rds")
p2_data <- p2_data %>% filter(!is.na(time_day))

p2_data %>% 
  group_by(id) %>% 
  filter(any(duplicated(time_day)) | any(diff(time_day) <= 0)) %>% 
  distinct(id)
```

## Observed Model
### Standardize Variables
```{r}
p2_data <- p2_data %>%
  mutate(across(c(esm_pa, zpos, zneg, zdis), scale))

p2_data %>%
  select(esm_pa, zpos, zneg, zdis) %>%
  psych::describe()
```

### Model Specification
```{r}
pos_ctsem <- "
# Measurement Model
posaff_B =~ esm_pa
posaff_W =~ esm_pa

# Between/Trend
posaff_B  ~  posaff_B     
posaff_B ~~  0*posaff_B # this is what tells model its between-person
posaff_B %~% posaff_B     

# Within (dynamic) factor
posaff_W  ~  posaff_W       
posaff_W ~~  posaff_W       
posaff_W %~% posaff_W       

# CINT
posaff_B ~ 1
"

pos_ctsem_syn <- ct_lavaan(pos_ctsem) 
```

### Fit Model
```{r}
#| eval: false
pos_ctsem_mod <- ctModel(
  type          = "ct",
  id = "id",
  time = "time_day",
  latentNames   = pos_ctsem_syn$latentNames,
  manifestNames = pos_ctsem_syn$manifestNames,
  LAMBDA        = pos_ctsem_syn$LAMBDA,
  DRIFT         = pos_ctsem_syn$DRIFT,
  DIFFUSION     = pos_ctsem_syn$DIFFUSION,
  T0VAR         = pos_ctsem_syn$T0VAR,
  CINT          = pos_ctsem_syn$CINT,
  T0MEANS       = pos_ctsem_syn$T0MEANS,
  MANIFESTMEANS = pos_ctsem_syn$MANIFESTMEANS,
  manifesttype  = pos_ctsem_syn$manifesttype,
  n.TIpred      = 3,
  TIpredNames   = c("zpos", "zneg", "zdis")
)

pos_ctsem_mod$pars[, c("zpos", "zneg", "zdis")] <- FALSE

target <- pos_ctsem_mod$pars$matrix == "DRIFT" &
          pos_ctsem_mod$pars$row    == "posaff_W" &
          pos_ctsem_mod$pars$col    == "posaff_W"

pos_ctsem_mod$pars[target, c("zpos", "zneg", "zdis")] <- TRUE

pos_ctsem_fit <- ctStanFit(
  datalong = p2_data, 
  ctstanmodel = pos_ctsem_mod,
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(pos_ctsem_fit, "02_files/pos_ctsem_fit.Rds")
```

### Evaluate Model Fit
```{r}
pos_ctsem_fit <- readRDS("02_files/pos_ctsem_fit.Rds")
```

#### Residual Auto-Correlation
```{r}
acf_pos_ctsem_fit <- readRDS("02_files/acf_pos_ctsem_fit.rds")
item_manifests <- pos_ctsem_syn$manifestNames
acf_pos_ctsem <- acf_pos_ctsem_fit$data

diag_dt_fit <- unique(
  acf_pos_ctsem[Variable %in% item_manifests,
                       .(TimeInterval, Variable, Q50 = `Q50%`, lo = `Q2.5%`, hi = `Q97.5%`, SignificanceLevel)]
)

ggplot(diag_dt_fit, aes(x = TimeInterval, y = Q50)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = .2) +
  geom_line() +
  geom_hline(aes(yintercept = SignificanceLevel), linetype = "dotted") +
  geom_hline(aes(yintercept = -SignificanceLevel), linetype = "dotted") +
  geom_hline(yintercept = 0, color = "grey50", linewidth = .3) +
  facet_wrap(~ Variable, ncol = 6, scales = "free_y") +
  labs(title = "Residual autocorrelation (item-level latent floor-effect model, diagonal)", y = "ACF", x = "Time interval (days)") +
  theme_minimal()
```

#### Posterior Predictive Check
```{r}
#| eval: false
pp_plot_pos_ctsem_fit <- ctPostPredPlots(pos_ctsem_fit)
saveRDS(pp_plot_pos_ctsem_fit, "02_files/pp_plot_pos_ctsem_fit.rds")
```

```{r}
pp_plot_pos_ctsem_fit <- readRDS("02_files/pp_plot_pos_ctsem_fit.rds")

for (panel_name in names(pp_plot_pos_ctsem_fit)) {
  cat("\n---", panel_name, "---\n")
  tryCatch(
    print(pp_plot_pos_ctsem_fit[[panel_name]]),
    error = function(e) {
      cat("  [", panel_name, "panel failed to render:", conditionMessage(e), "]\n")
    }
  )
}
```

:::callout-note
Overall, the model's expected values and observed values suggest great fit.
:::

### Results

#### Auto-Effect Visual
```{r}
set.seed(1111)
ct_effects_plot(
  pos_ctsem_fit,
  effects = c(
    "posaff_W>posaff_W"),
  times = seq(0, 2, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Positive Affect",
  legend_labels = c(
    "Positive Affect -> Positive Affect"),
  latentNames = pos_ctsem_syn$latentNames   # <- add this
)
```

#### Main Effects
```{r}
pos_ctsem_fit <- readRDS("02_files/pos_ctsem_fit.Rds")
pos_ctsem_res <- summary(pos_ctsem_fit)
pos_ctsem_res$parmatrices %>%
  filter(matrix == "DRIFT") %>%
  filter(row == col)
```

:::callout-note
The first parameter represents the overall between-person detrend of Positive Affect (-0.03, [-.12, -0.006]). This means that the detrend is fairly weak, and Positive Affect as a "trait" is fairly stable.

The second parameter represents the within-person dynamic return of PA to equilibrium (-4.29 [-5.43, -3.33]). What does this mean practically? This tells us how fast a process returns to equilibrium.

We can actually calculate the half-life using the following:
:::

```{r}
days <- log(0.5)/-4.29
days

days*24
```

:::callout-note
Interpretation: For a given deivation from a person's stable, trait-level positive affect, half of that deviation would dissipate within approximately 3.9 hours--assuming no other force intervened.
:::

```{r}
pos_ctsem_res$parmatrices %>%
  filter(matrix == "dtDRIFT") %>%
  filter(row == col)
```

:::callout-note
When dtDRIFT == 1 (1 day/24 hours), only ~1.6% of the original deviation on PA would remain.
:::

### Cross-level Interaction
#### Auto-Effect
```{r}
pos_ctsem_res$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("auto_posaff_W", param))
```

:::callout-note
Similar to the interpretation above, we find significant cross-level interactions. A bigger `negative` coefficient suggests the time invariant variable predicted **faster** decay.

1.  Positive Affect (MSS) had the largest negative association (-2.29 [-3.24, -1.35]) with the auto-effect of PA. **In other words**, greater MSS-PA is associated with a faster decay in within-PA.
2.  Likewise, greater MSS-Negative Affect was also associated with faster decay (-1.76 [-2.61, -0.95]). 
3.  However, greater MSS-Disorganized Schitzophrenia was associated with **slower** decay in PA (0.82 [0.02, 1.59]).
:::

#### Diffusion/Volatility
```{r}
pos_ctsem_res$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("diff_posaff_W", param))
```

:::callout-note
Diffiusion represents the `volatility` not accounted for by the either the between or wihtin-person AR effects. 

1.  MSS-Positive Affect had the largest positive association (0.41 [0.26, 0.57]) the diffusion of within-PA.
2.  Likewise, greater MSS-Negative Affect was also associated with the diffusion of within-PA (0.29 [0.16, 0.41]). 
3.  However, greater MSS-Disorganized Schitzophrenia was associated with **lower** diffusion of within-PA (-0.12 [-0.29, 0.06]); although this was **not a credible** association.
:::


