---
title: "Positive Affect"
format:
  html:
    toc: true
    toc-depth: 6
    lightbox: auto   # click any figure to enlarge / zoom
code-line-numbers: true
code-annotations: true
editor_options: 
  chunk_output_type: console
execute:
  warning: FALSE
---

:::callout-note
## Seungju's Note:
Hi! I wont provide notes for all chapters, but do so for this one. My notes are under the blue tag.
:::

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/mod_plot.R")
source("cust_funcs/ct_dpars_plot.R")
source("cust_funcs/ct_mod_grid.R")
source("cust_funcs/ct_halflife.R")
source("cust_funcs/ct_sig_table.R")
```

```{r}
#| include: false
p2_data <- readRDS("data/p1_data.Rds") %>%
  mutate(esm24_ord = as.numeric(esm24))   # raw 1-7 codes for the ordinal esm24 model (never scaled)
p2_data %>% 
  group_by(id) %>% 
  filter(any(duplicated(time_day)) | any(diff(time_day) <= 0)) %>% 
  distinct(id)
```

### Standardize Variables

:::callout-note
Let's standardize the variables:
:::
```{r}
p2_data <- p2_data %>%
  mutate(across(c(esm_pa, zpos, zneg, zdis, esm24, esm25), scale))

p2_data %>%
  select(esm_pa, zpos, zneg, zdis) %>%
  psych::describe()
```

## Positive Affect (Auto-Effect + Trend)

### Model Specification
```{r}
#| code-fold: false
# Per-model data: one row per id x time_day (no zero intervals); drop beeps
# where every outcome is missing.
pa_trend_data <- p2_data %>%
  group_by(id) %>% filter(!duplicated(time_day)) %>% ungroup() %>%
  filter(!(is.na(esm_pa))) %>%
  mutate(across(c(esm_pa, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

pa_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_pa"),
  latentNames   = c("pa", "pa_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(0),   # 0 continuous, 1 binary, 4 censored
  censormin     = c(-Inf),
  censormax     = c(Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(1), diag(1)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "pa_pa"         , 0,
    0               , "drift_pa_trend"),
    2, 2, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_pa", 0,
    0        , 0),
    2, 2, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_pa", 0,
    0         , 0),
    2, 2, byrow = TRUE),
  T0MEANS = c(0, "T0m_pa_trend"),
  CINT    = c(0, "cint_pa_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_pa"),
    1, 1, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
pa_trend_mod$pars$indvarying <- pa_trend_mod$pars$param %in% c("T0m_pa_trend", "cint_pa_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
pa_trend_mod$pars[, eff] <- FALSE
pa_trend_mod$pars[pa_trend_mod$pars$matrix == "DRIFT" &
               pa_trend_mod$pars$param %in% c("pa_pa"), eff] <- TRUE

pa_trend_mod$pars[pa_trend_mod$pars$indvarying | rowSums(pa_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(pa_trend_mod)
```

:::callout-note
## Let's breakdown the model:

**How is `positive-affect` modeled?**

PA is decomposed into two latent variables: the dynamic momentary changes (`pa`) and a slow-moving personal baseline (`pa_trend`).

**The `pa_trend` is a new addition.**

The central idea is this: We know that the dynamic momentary changes are taking place, and that the overall level of positive affect may decrease/detrend over time (e.g., very sensitive at the start of the study, a very positive start to the week). 

In essence the `pa_trend` is a latent "random intercept" that captures stable trait, but is allowed to drift slowly. The dynamic momentary changes represent residual variance changes. This is very similar to the `Residual` DSEM, which models time as a (linear) covariate. We let the data determine the shape of how person-level `pa` detrends over time.

**Other Model Specifications:**

**Core idea:** each PA rating = slow-moving personal baseline (`pa_trend`) + momentary state (`pa`) + beep-specific noise.

- **Time:** continuous (`time_day`), so unequal gaps between beeps are handled. Carry-over across a gap of Δt = exp(drift × Δt).
- **LAMBDA `[1 1]`:** observed PA is the sum of the baseline and the momentary state. Both loadings are fixed to 1.
- **DRIFT**
  - `pa_pa`: how fast a PA deviation fades back to baseline. More negative = faster recovery; closer to 0 = more inertia. Half-life = ln(2)/|drift|.
  - `drift_pa_trend`: shapes how the stable-detrend curves over the week.
  - Off-diagonals are fixed to 0, so baseline and momentary state don't influence each other.
- **DIFFUSION**
  - `diff_pa`: size of random shocks to the momentary state (events that push PA up or down). This is essentially innovation or residual variance.
  - Fixed to 0 for the trend, so the baseline moves smoothly, without shocks.
- **T0VAR**
  - `T0var_pa`: spread of the momentary state at each person's first beep.
  - Fixed to 0 for the trend, because its starting differences come from random T0MEANS.
- **T0MEANS**
  - `pa` is fixed to 0 (a deviation from baseline).
  - `T0m_pa_trend` is free and random: each person's starting baseline.
- **CINT**
  - `pa` is fixed to 0, so the momentary state is always pulled back to the person's own baseline.
  - `cint_pa_trend` is free and random. With `drift_pa_trend`, it sets where each person's baseline is heading (long-run level = −cint/drift).
- **MANIFESTMEANS = 0:** the level of PA is carried by the trend, so it isn't estimated twice.
- **MANIFESTVAR `mvar_pa`:** measurement noise that affects a single beep and doesn't carry over.
- **Random effects:** only `T0m_pa_trend` and `cint_pa_trend` (person-specific start and direction of the baseline). All other parameters are shared across people.
- **Schizotypy (zpos, zneg, zdis):** moderates only `pa_pa`. It tests whether schizotypy changes PA inertia, not whether it predicts overall PA level.
- **Estimation:** maximum a posteriori.

| Piece | Setting | Meaning |
|---|---|---|
| LAMBDA | [1 1] | Observed PA = baseline + momentary state |
| DRIFT `pa_pa` | free | How fast a PA bump fades (half-life) |
| DRIFT `drift_pa_trend` | free | Curvature of the week-long baseline |
| DIFFUSION `diff_pa` | free | Size of random shocks to momentary PA |
| DIFFUSION trend | 0 | Baseline is smooth |
| T0VAR `T0var_pa` | free | First-beep deviation from baseline |
| T0MEANS `T0m_pa_trend` | free, random | Person's starting baseline |
| CINT `cint_pa_trend` | free, random | Where the person's baseline is heading |
| CINT `pa` | 0 | Momentary state returns to baseline |
| MANIFESTMEANS | 0 | Level carried by the trend |
| MANIFESTVAR `mvar_pa` | free | One-beep noise that doesn't carry over |
| TIpreds | on `pa_pa` only | Does schizotypy change PA inertia? |
:::

### Fit Model
```{r}
#| eval: false
# ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
pa_trend_fit <- ctFit(
  datalong = pa_trend_data,
  model    = pa_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(pa_trend_fit, "02_files/pa_trend_fit.Rds")
beepr::beep(8)
```

```{r}
pa_trend_fit <- readRDS("02_files/pa_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
pa_trend_fit <- ctGenerateFromFit(pa_trend_fit, nsamples = 100)
pp_pa_trend <- ctPostPredPlots(pa_trend_fit)
saveRDS(pp_pa_trend, "02_files/pp_pa_trend.rds")
pa_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

:::callout-note
Let's break down model fit. 

Unlike traditional SEM software, `ctsem` doesn't provide fit indices, which is perfectly fine since we all know fit index cutoffs can be misleading. In `ctsem` we use visual plots which can demonstrate how well the estimated parameters replicate observed data.
:::

```{r}
pp_pa_trend <- readRDS("02_files/pp_pa_trend.rds")
pp_pa_trend$Density
```

:::callout-note
The density plot shows the distribution of PA values in the observed data compared to data simulated from the model. **Ideally** the two curves should overlap, which signals the model is reproducing the observed data correctly.

If the location or width is off, the model is getting the overall PA level or spread wrong. If only the shape is off (e.g., skew or a pile-up at the floor), the normal distribution assumption doesn't hold. This matters because a mis-specified distribution distorts the likelihood, which can bias the variance terms and, in turn, the auto-effect.
:::


```{r}
pp_pa_trend$MeanTrajectory
```

:::callout-note
The mean trajectory plot shows average PA across the study for the observed data versus the model, with a 95% band. **Ideally** the observed line stays inside the band for the whole week.

A systematic gap, especially early or late in the study, means the model is missing how average PA changes over time. This matters because any time trend the model misses gets absorbed into the dynamic process, which usually inflates the auto-effect (PA looks more "sticky" than it really is).
:::

```{r}
pp_pa_trend$LaggedCovariance_esm_pa
```

:::callout-note
The lagged covariance plot shows how strongly PA correlates with itself 0–5 beeps later, observed versus model-implied. **Ideally** the observed points fall inside the model bars at every lag.

Points above the bars mean PA is more persistent than the model allows; points below mean the model is too persistent. A misfit at short lags points to the auto-effect or diffusion, while a misfit at longer lags points to the trend or random effects. This is the most important check, because the auto-effect and its schizotypy moderation are estimated directly from this carry-over pattern. If the model can't reproduce it, those estimates are likely biased.
:::

```{r}
pp_pa_trend$SubjectLogLik
```

:::callout-note
The subject log-likelihood plot shows how well the model fits each person, compared to what the model expects. **Ideally** the two distributions overlap.

A long tail of very low values means a subset of people fit poorly (e.g., unusual response patterns or very different dynamics). This matters because a few badly fitting people can pull the population estimates toward them, so it's worth checking who they are before changing the model.
:::


### Results Table
```{r}
ct_sig_table(pa_trend_fit)
```

### Half-Life

:::callout-note
It's showing here, if you experience an increase in positive affect, the self-predictive power will dissipate to half it's life by 5.2 hours.
:::

```{r}
ct_halflife(pa_trend_fit, c("pa", "pa_trend"), pattern = NULL) %>%
  ct_sig_gt(lower = "drift_2.5", upper = "drift_97.5")
```

### Auto-Effects
:::callout-note
Time-scale is in days.
:::

```{r}
#| eval: false
set.seed(1111)
dp_pa_trend <- ct_dpars_plot(pa_trend_fit,
  type     = "auto",   # auto-effects only (no cross-effects in this model)
  exclude  = c("pa_trend"),   # dynamic process(es) only
  times    = seq(0, 2, 0.02),
  nsamples = 100,
  standardise = TRUE)
saveRDS(dp_pa_trend, "02_files/dp_pa_trend.rds")
beepr::beep(8)
```

```{r}
dp_pa_trend <- readRDS("02_files/dp_pa_trend.rds")
dp_pa_trend$plot_auto
```

### Moderation

:::callout-note
Unlike traditional regression models, it doesn't make sense to predict an auto-drift. Instead, it's more informative to see how TI-predictors are associated by looking at a cross-interaction.
:::

#### TIpred Effects
```{r}
summary(pa_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_pa_trend <- ct_mod_grid(
  pa_trend_fit,
  latentNames = c("pa", "pa_trend"),
  effects     = c("pa"),
  tipreds     = c("zneg", "zdis"),
  labels      = c(zneg = "Negative Schizotypy",
                  zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.04),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_pa_trend, "02_files/mod_pa_trend.rds")
beepr::beep(8)
```

```{r}
mod_pa_trend <- readRDS("02_files/mod_pa_trend.rds")
```

##### ZNEG
```{r}
#| fig-width: 6
#| fig-height: 4
patchwork::wrap_plots(lapply(mod_pa_trend$zneg, `[[`, "plot"), ncol = 1, guides = "collect")
```

##### ZDIS
```{r}
#| fig-width: 6
#| fig-height: 4
patchwork::wrap_plots(lapply(mod_pa_trend$zdis, `[[`, "plot"), ncol = 1, guides = "collect")
```

## Positive Situation (esm24)

:::callout-note
This is a bivariate VAR model. Same as above, each construct has its dynamic momentary variable and a person stable detrend variable. 

The key difference in this model is that we allow `PA` to predict positive situations `psit`, and vice-versa. We also estimate the residual covariance between `PA` and `psit`.

The latent detrend variables are not correlated with one another.
:::

### Model Specification
```{r}
# Per-model data: one row per id x time_day (no zero intervals) and drop
# beeps where both outcomes are missing (saves memory / time).
sit_trend_data <- p2_data %>%
  group_by(id) %>% filter(!duplicated(time_day)) %>% ungroup() %>%
  filter(!(is.na(esm_pa) & is.na(esm24))) %>%
  mutate(across(c(esm_pa, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

sit_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_pa", "esm24"),
  latentNames   = c("pa", "psit", "pa_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (psit_pa = psit -> pa);
  # trend factors only have their own (slow) drift, no cross-links
  DRIFT = matrix(c(
    "pa_pa",      "psit_pa",      0,                0,
    "pa_psit",    "psit_psit",    0,                0,
    0,            0,              "drift_pa_trend", 0,
    0,            0,              0,                "drift_psit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only (trends are smooth) (correlation fixed to 0)
  DIFFUSION = matrix(c(
    "diff_pa",      0,           0, 0,
    0, "diff_psit", 0, 0,
    0,              0,           0, 0,
    0,              0,           0, 0), 4, 4, byrow = TRUE),
  # T0VAR -- initial within-person deviations; trend starting points are
  # captured by the random T0MEANS instead
  T0VAR = matrix(c(
    "T0var_pa",      0,             0, 0,
    "T0var_pa_psit", "T0var_psit", 0, 0,
    0,               0,             0, 0,
    0,               0,             0, 0), 4, 4, byrow = TRUE),
  # Trend factors: person-specific starting level (T0MEANS) and
  # person-specific level the trend drifts toward (CINT)
  T0MEANS = c(0, 0, "T0m_pa_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, "cint_pa_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  # MANIFESTVAR: occasion-specific error variances + covariance
  # (same-moment association is carried here; DIFFUSION correlation fixed to 0)
  MANIFESTVAR = matrix(c(
    "mvar_pa",      0,
    "mvar_pa_psit", "mvar_psit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default);
# auto-/cross-effects are fixed across people.
sit_trend_mod$pars$indvarying <- sit_trend_mod$pars$param %in%
  c("T0m_pa_trend", "T0m_psit_trend", "cint_pa_trend", "cint_psit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects);
# not the trend drifts, trend T0MEANS/CINT, DIFFUSION or measurement part
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
sit_trend_mod$pars[, eff] <- FALSE
sit_trend_mod$pars[sit_trend_mod$pars$matrix == "DRIFT" &
               sit_trend_mod$pars$param %in% c("pa_pa", "psit_pa", "pa_psit", "psit_psit"), eff] <- TRUE

sit_trend_mod$pars[sit_trend_mod$pars$indvarying | rowSums(sit_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(sit_trend_mod)
```

### Fit Model
```{r}
#| eval: false
# ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
sit_trend_fit <- ctFit(
  datalong = sit_trend_data,
  model    = sit_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(sit_trend_fit, "02_files/sit_trend_fit.Rds")

```

```{r}
sit_trend_fit <- readRDS("02_files/sit_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
sit_trend_fit <- ctGenerateFromFit(sit_trend_fit, nsamples = 100)
pp_sit_trend <- ctPostPredPlots(sit_trend_fit)
saveRDS(pp_sit_trend, "02_files/pp_sit_trend.rds")
beepr::beep(8)
```

```{r}
pp_sit_trend <- readRDS("02_files/pp_sit_trend.rds")
pp_sit_trend$Density
pp_sit_trend$MeanTrajectory
pp_sit_trend$LaggedCovariance_esm_pa
pp_sit_trend$LaggedCovariance_esm24
pp_sit_trend$SubjectLogLik
```

### Results Table

:::callout-note
You will find several things below. We are most interested in the **drift** parameters, specifically the auto and cross-drifts.

Results show `psit` has a significant cross-effect on `pa`, such that greater `psit` is assocaited with lower `pa`. `pa` did not predict `psit`.
:::

```{r}
ct_sig_table(sit_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_sit_trend <- ct_dpars_plot(sit_trend_fit,
  exclude  = c("pa_trend", "psit_trend"),   # dynamic processes only
  times    = seq(0, 3, 0.001),
  nsamples = 100,
  standardise = T)
saveRDS(dp_sit_trend, "02_files/dp_sit_trend.rds")
beepr::beep(8)
```

:::callout-note
Observe: the decay of `psit` is faster than `pa`.
:::

```{r}
dp_sit_trend <- readRDS("02_files/dp_sit_trend.rds")
dp_sit_trend$plot_auto
```

:::callout-important
This is the true power of **CT-models**. Not only do we estimate a cross-effect, but also we can see when `psit`'s predictive effect on `pa` is the strongest!

It peaks at 0.26 days (6.2 hrs), and recedes from there. If desired, we can also estimate the cross-lagged effect of any order (e.g., lag(1 day), lag(4 days), lag(45.1 hrs)).
:::

```{r}
dp_sit_trend$plot_cross
dp_sit_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```


### Moderation

:::callout-note
Here we observe that only Positive Schizotypy had a significant association.
:::

#### TIpred Effects
```{r}
summary(sit_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_sit_trend <- ct_mod_grid(
  sit_trend_fit,
  latentNames = c("pa", "psit", "pa_trend", "psit_trend"),
  effects     = c("pa", "psit>pa", "pa>psit", "psit"),
  tipreds     = c("zpos", "zdis"),
  labels      = c(zpos = "Positive Schizotypy",
                  zdis = "Disorganized Schizotypy"),
  times       = seq(0, 3, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_sit_trend, "02_files/mod_sit_trend.rds")
beepr::beep(8)
```

##### ZPOS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_sit_trend <- readRDS("02_files/mod_sit_trend.rds")
mod_sit_trend$zpos$`psit (auto`$plot
```

##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_sit_trend$zdis$`psit -> pa`$plot
```

## Stressful Situation (esm25)

### Model Specification
```{r}
# Per-model data: one row per id x time_day (no zero intervals) and drop
# beeps where both outcomes are missing (saves memory / time).
str_trend_data <- p2_data %>%
  group_by(id) %>% filter(!duplicated(time_day)) %>% ungroup() %>%
  filter(!(is.na(esm_pa) & is.na(esm25))) %>%
  mutate(across(c(esm_pa, esm25, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

str_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_pa", "esm25"),
  latentNames   = c("pa", "ssit", "pa_trend", "ssit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (ssit_pa = ssit -> pa);
  # trend factors only have their own (slow) drift, no cross-links
  DRIFT = matrix(c(
    "pa_pa",      "ssit_pa",      0,                0,
    "pa_ssit",    "ssit_ssit",    0,                0,
    0,            0,              "drift_pa_trend", 0,
    0,            0,              0,                "drift_ssit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only (trends are smooth) (correlation fixed to 0)
  DIFFUSION = matrix(c(
    "diff_pa",      0,           0, 0,
    0, "diff_ssit", 0, 0,
    0,              0,           0, 0,
    0,              0,           0, 0), 4, 4, byrow = TRUE),
  # T0VAR -- initial within-person deviations; trend starting points are
  # captured by the random T0MEANS instead
  T0VAR = matrix(c(
    "T0var_pa",      0,             0, 0,
    "T0var_pa_ssit", "T0var_ssit", 0, 0,
    0,               0,             0, 0,
    0,               0,             0, 0), 4, 4, byrow = TRUE),
  # Trend factors: person-specific starting level (T0MEANS) and
  # person-specific level the trend drifts toward (CINT)
  T0MEANS = c(0, 0, "T0m_pa_trend", "T0m_ssit_trend"),
  CINT    = c(0, 0, "cint_pa_trend", "cint_ssit_trend"),
  MANIFESTMEANS = 0,
  # MANIFESTVAR: occasion-specific error variances + covariance
  # (same-moment association is carried here; DIFFUSION correlation fixed to 0)
  MANIFESTVAR = matrix(c(
    "mvar_pa",      0,
    "mvar_pa_ssit", "mvar_ssit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default);
# auto-/cross-effects are fixed across people.
str_trend_mod$pars$indvarying <- str_trend_mod$pars$param %in%
  c("T0m_pa_trend", "T0m_ssit_trend", "cint_pa_trend", "cint_ssit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects);
# not the trend drifts, trend T0MEANS/CINT, DIFFUSION or measurement part
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
str_trend_mod$pars[, eff] <- FALSE
str_trend_mod$pars[str_trend_mod$pars$matrix == "DRIFT" &
               str_trend_mod$pars$param %in% c("pa_pa", "ssit_pa", "pa_ssit", "ssit_ssit"), eff] <- TRUE

str_trend_mod$pars[str_trend_mod$pars$indvarying | rowSums(str_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(str_trend_mod)
```

### Fit Model
```{r}
#| eval: false
# ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
str_trend_fit <- ctFit(
  datalong = str_trend_data,
  model    = str_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(str_trend_fit, "02_files/str_trend_fit.Rds")

```

```{r}
str_trend_fit <- readRDS("02_files/str_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
str_trend_fit <- ctGenerateFromFit(str_trend_fit, nsamples = 100)
pp_str_trend <- ctPostPredPlots(str_trend_fit)
saveRDS(pp_str_trend, "02_files/pp_str_trend.rds")
str_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_str_trend <- readRDS("02_files/pp_str_trend.rds")
pp_str_trend$Density
pp_str_trend$MeanTrajectory
pp_str_trend$LaggedCovariance_esm_pa
pp_str_trend$LaggedCovariance_esm25
pp_str_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(str_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_str_trend <- ct_dpars_plot(str_trend_fit,
  exclude  = c("pa_trend", "ssit_trend"),   # dynamic processes only
  times    = seq(0, 2, 0.001),
  nsamples = 100,
  standardise = TRUE)
saveRDS(dp_str_trend, "02_files/dp_str_trend.rds")
beepr::beep(8)
```

```{r}
dp_str_trend <- readRDS("02_files/dp_str_trend.rds")
dp_str_trend$plot_auto
dp_str_trend$plot_cross
dp_str_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(str_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_str_trend <- ct_mod_grid(
  str_trend_fit,
  latentNames = c("ssit", "pa"),
  effects     = c("ssit", "pa"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.001),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_str_trend, "02_files/mod_str_trend.rds")
beepr::beep(8)
```
```{r}
mod_str_trend <- readRDS("02_files/mod_str_trend.rds")
```

##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
patchwork::wrap_plots(lapply(mod_str_trend$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```

```{r}
#| include: false
saveRDS(p2_data, "data/p2_data.Rds")
```

