---
title: "Positive Affect"
format:
  html:
    toc: true
    toc-depth: 6
code-line-numbers: true
code-annotations: true
editor_options: 
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/mod_plot.R")
```

```{r}
#| include: false
p2_data <- readRDS("data/p1_data.Rds")
p2_data %>% 
  group_by(id) %>% 
  filter(any(duplicated(time_day)) | any(diff(time_day) <= 0)) %>% 
  distinct(id)
```

## Observed Model
### Standardize Variables
```{r}
p2_data <- p2_data %>%
  mutate(across(c(esm_pa, zpos, zneg, zdis), scale))

p2_data %>%
  select(esm_pa, zpos, zneg, zdis) %>%
  psych::describe()
```

### Model Specification
```{r}
pos_ctsem <- "
# Cross-level interaction declarations -- which TIpreds exist, and (inline
# below) which DRIFT parameter(s) each one is allowed to moderate. Only
# posaff_W (the within-person factor) gets TIpred moderation here --
# posaff_B (the between-person factor) is left unrestricted/untouched, same
# as before.
TIPRED: zpos, zneg, zdis

# Measurement Model
posaff_B =~ esm_pa
posaff_W =~ esm_pa

# Between/Trend
posaff_B  ~  0*posaff_B     
posaff_B ~~  0*posaff_B # this is what tells model its between-person
posaff_B %~% posaff_B     

# Within (dynamic) factor
posaff_W  ~  posaff_W + posaff_W:zpos + posaff_W:zneg + posaff_W:zdis
posaff_W ~~  posaff_W       
posaff_W %~% posaff_W       

# CINT
posaff_B ~ 0
"

pos_ctsem_syn <- ct_lavaan(pos_ctsem, data = p2_data, id = "id", time = "time_day")
pos_ctsem_mod <- pos_ctsem_syn$mod
ctModelLatexHTML(pos_ctsem_mod)
```

### Fit Model
```{r}
#| eval: false
pos_ctsem_fit <- ctFit(
  datalong = p2_data, 
  ctstanmodel = pos_ctsem_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(pos_ctsem_fit, "02_files/pos_ctsem_fit.Rds")

acf_pos_ctsem_fit <- ctsem::ctACFresiduals(pos_ctsem_fit)
saveRDS(acf_pos_ctsem_fit, "02_files/acf_pos_ctsem_fit.rds")
beepr::beep(8)
```

### Evaluate Model Fit
```{r}
pos_ctsem_fit <- readRDS("02_files/pos_ctsem_fit.Rds")
summary(pos_ctsem_fit)
ctModelLatexHTML(pos_ctsem_fit)
```

#### Posterior Predictive Check
```{r}
#| eval: false
pp_plot_pos_ctsem_fit <- ctPostPredPlots(pos_ctsem_fit)
saveRDS(pp_plot_pos_ctsem_fit, "02_files/pp_plot_pos_ctsem_fit.rds")
beepr::beep(8)
```

```{r}
pp_plot_pos_ctsem_fit <- readRDS("02_files/pp_plot_pos_ctsem_fit.rds")
pp_plot_pos_ctsem_fit$Density
pp_plot_pos_ctsem_fit$MeanTrajectory
pp_plot_pos_ctsem_fit$LaggedCovariance_esm_pa
pp_plot_pos_ctsem_fit$SubjectLogLik
```

:::callout-note
Overall, the model's expected values and observed values suggest great fit.
:::

### Results

#### Auto-Effect Visual
```{r}
set.seed(1111)
ct_effects_plot(
  pos_ctsem_fit,
  effects = c(
    "posaff_W>posaff_W"),
  times = seq(0, 2, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Positive Affect",
  legend_labels = c(
    "Positive Affect -> Positive Affect"),
  latentNames = pos_ctsem_syn$latentNames   # <- add this
)
```

:::callout-note
You are looking at a 2 day timeframe. We can request more, but as you can see, it returns to equilibrium fairly quickly.
:::

#### Main Effects
```{r}
pos_ctsem_fit <- readRDS("02_files/pos_ctsem_fit.Rds")
summary(pos_ctsem_fit)$parmatrices %>%
  filter(matrix == "DRIFT") %>%
  filter(row == col)
```

:::callout-note
The first parameter represents the overall between-person detrend of Positive Affect (0), which we set as a latent random intercept that capture the stable trait. 

The second parameter represents the within-person dynamic return of PA to equilibrium (-3.703 [-4.976, -2.581]). What does this mean practically? This tells us how fast a process returns to equilibrium.

We can actually calculate the **half-life** using the following:
:::

```{r}
days <- log(0.5)/-3.703
days

days*24
```

:::callout-note
Interpretation: For a given deivation from a person's stable, trait-level positive affect, half of that deviation would dissipate within approximately **4.49** hours--assuming no other force intervened.
:::

### *Cross-level Interaction
#### Auto-Effect
```{r}
summary(pos_ctsem_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("auto_posaff_W", param)) %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  gt::gt()
```

:::callout-note
Similar to the interpretation above, we find one significant cross-level interactions. A bigger `negative` coefficient suggests the time invariant variable predicted **faster** decay.

1.  Positive-Z was **not significant** moderator (-0.201 [-0.536, 0.155]) with the auto-effect of PA.
2.  Greater Negative-Z was **not significant** a moderator (-0.353 [-0.732, 0.002]). 
3.  However, Disorganized-Z was significantly associated with **slower** decay in PA (0.457 [0.110, 0.832]).
:::

#### ZDIS
```{r}
#| eval: false
zdis_pa_cross <- plot_ribbon_multi(
  pos_ctsem_fit,
  tipred_name = "zdis",
  times = seq(0, 1, 0.05),
  row = 2, col = 2,
  nsamp_use = 200,
  x_lab = "Time (days)",
  y_lab = "Positive Affect (Within-Person)",
  legend_title = "Disorganized Schitzotypy",
  line_width = 0.5,
  bound_width = 0.3,
  ribbon_alpha = 0.1
)
saveRDS(zdis_pa_cross, "02_files/zdis_pa_cross.rds")
```

```{r}
zdis_pa_cross <- readRDS("02_files/zdis_pa_cross.rds")
zdis_pa_cross$plot
```

:::callout-note
Higher Dis-Z demonstrates slower decay, while lower Dis-Z demonstrates comparable decay to median Dis-Z.
:::

```{r}
#| include: false
saveRDS(p2_data, "data/p2_data.Rds")
```

