---
title: "Positive Affect"
format:
  html:
    toc: true
    toc-depth: 6
    lightbox: auto   # click any figure to enlarge / zoom
code-line-numbers: true
code-annotations: true
editor_options: 
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/mod_plot.R")
source("cust_funcs/ct_dpars_plot.R")
source("cust_funcs/ct_mod_grid.R")
source("cust_funcs/ct_halflife.R")
source("cust_funcs/ct_sig_table.R")
```

```{r}
#| include: false
p2_data <- readRDS("data/p1_data.Rds") %>%
  mutate(esm24_ord = as.numeric(esm24))   # raw 1-7 codes for the ordinal esm24 model (never scaled)
p2_data %>% 
  group_by(id) %>% 
  filter(any(duplicated(time_day)) | any(diff(time_day) <= 0)) %>% 
  distinct(id)
```

### Standardize Variables
```{r}
p2_data <- p2_data %>%
  mutate(across(c(esm_pa, zpos, zneg, zdis, esm24, esm25), scale))

p2_data %>%
  select(esm_pa, zpos, zneg, zdis) %>%
  psych::describe()
```

## Positive Affect (Auto-Effect + Trend)

### Model Specification
```{r}
# Per-model data: one row per id x time_day (no zero intervals); drop beeps
# where every outcome is missing.
pa_trend_data <- p2_data %>%
  group_by(id) %>% filter(!duplicated(time_day)) %>% ungroup() %>%
  filter(!(is.na(esm_pa))) %>%
  mutate(across(c(esm_pa, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

pa_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_pa"),
  latentNames   = c("pa", "pa_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(0),   # 0 continuous, 1 binary, 4 censored
  censormin     = c(-Inf),
  censormax     = c(Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(1), diag(1)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "pa_pa"         , 0,
    0               , "drift_pa_trend"),
    2, 2, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_pa", 0,
    0        , 0),
    2, 2, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_pa", 0,
    0         , 0),
    2, 2, byrow = TRUE),
  T0MEANS = c(0, "T0m_pa_trend"),
  CINT    = c(0, "cint_pa_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_pa"),
    1, 1, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
pa_trend_mod$pars$indvarying <- pa_trend_mod$pars$param %in% c("T0m_pa_trend", "cint_pa_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
pa_trend_mod$pars[, eff] <- FALSE
pa_trend_mod$pars[pa_trend_mod$pars$matrix == "DRIFT" &
               pa_trend_mod$pars$param %in% c("pa_pa"), eff] <- TRUE

pa_trend_mod$pars[pa_trend_mod$pars$indvarying | rowSums(pa_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(pa_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
pa_trend_fit <- ctFit(
  datalong = pa_trend_data,
  model    = pa_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(pa_trend_fit, "02_files/pa_trend_fit.Rds")
beepr::beep(8)
```

```{r}
pa_trend_fit <- readRDS("02_files/pa_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
pa_trend_fit <- ctGenerateFromFit(pa_trend_fit, nsamples = 100)
pp_pa_trend <- ctPostPredPlots(pa_trend_fit)
saveRDS(pp_pa_trend, "02_files/pp_pa_trend.rds")
pa_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_pa_trend <- readRDS("02_files/pp_pa_trend.rds")
pp_pa_trend$Density
pp_pa_trend$MeanTrajectory
pp_pa_trend$LaggedCovariance_esm_pa
pp_pa_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(pa_trend_fit)
```

### Half-Life
```{r}
ct_halflife(pa_trend_fit, c("pa", "pa_trend"), pattern = NULL) %>%
  ct_sig_gt(lower = "drift_2.5", upper = "drift_97.5")
```

### Auto-Effects
```{r}
#| eval: false
set.seed(1111)
dp_pa_trend <- ct_dpars_plot(pa_trend_fit,
  type     = "auto",   # auto-effects only (no cross-effects in this model)
  exclude  = c("pa_trend"),   # dynamic process(es) only
  times    = seq(0, 2, 0.02),
  nsamples = 100)
saveRDS(dp_pa_trend, "02_files/dp_pa_trend.rds")
beepr::beep(8)
```

```{r}
dp_pa_trend <- readRDS("02_files/dp_pa_trend.rds")
dp_pa_trend$plot_auto
```

### Moderation
#### TIpred Effects
```{r}
summary(pa_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_pa_trend <- ct_mod_grid(
  pa_trend_fit,
  latentNames = c("pa", "pa_trend"),
  effects     = c("pa"),
  tipreds     = c("zneg", "zdis"),
  labels      = c(zneg = "Negative Schizotypy",
                  zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.04),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_pa_trend, "02_files/mod_pa_trend.rds")
beepr::beep(8)
```

```{r}
mod_pa_trend <- readRDS("02_files/mod_pa_trend.rds")
```

##### ZNEG
```{r}
#| fig-width: 6
#| fig-height: 4
patchwork::wrap_plots(lapply(mod_pa_trend$zneg, `[[`, "plot"), ncol = 1, guides = "collect")
```

##### ZDIS
```{r}
#| fig-width: 6
#| fig-height: 4
patchwork::wrap_plots(lapply(mod_pa_trend$zdis, `[[`, "plot"), ncol = 1, guides = "collect")
```

## Positive Situation (esm24)

### Model Specification
```{r}
# Per-model data: one row per id x time_day (no zero intervals) and drop
# beeps where both outcomes are missing (saves memory / time).
sit_trend_data <- p2_data %>%
  group_by(id) %>% filter(!duplicated(time_day)) %>% ungroup() %>%
  filter(!(is.na(esm_pa) & is.na(esm24))) %>%
  mutate(across(c(esm_pa, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

sit_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_pa", "esm24"),
  latentNames   = c("pa", "psit", "pa_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (psit_pa = psit -> pa);
  # trend factors only have their own (slow) drift, no cross-links
  DRIFT = matrix(c(
    "pa_pa",      "psit_pa",      0,                0,
    "pa_psit",    "psit_psit",    0,                0,
    0,            0,              "drift_pa_trend", 0,
    0,            0,              0,                "drift_psit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only (trends are smooth)
  DIFFUSION = matrix(c(
    "diff_pa",      0,           0, 0,
    "diff_pa_psit", "diff_psit", 0, 0,
    0,              0,           0, 0,
    0,              0,           0, 0), 4, 4, byrow = TRUE),
  # T0VAR -- initial within-person deviations; trend starting points are
  # captured by the random T0MEANS instead
  T0VAR = matrix(c(
    "T0var_pa",      0,             0, 0,
    "T0var_pa_psit", "T0var_psit", 0, 0,
    0,               0,             0, 0,
    0,               0,             0, 0), 4, 4, byrow = TRUE),
  # Trend factors: person-specific starting level (T0MEANS) and
  # person-specific level the trend drifts toward (CINT)
  T0MEANS = c(0, 0, "T0m_pa_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, "cint_pa_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  # MANIFESTVAR: measurement error incl. its covariance (same-beep response
  # style / shared occasion error). Without it the shock correlation goes to
  # ~.99 and the cross-effects compensate.
  MANIFESTVAR = matrix(c(
    "mvar_pa",      0,
    "mvar_pa_psit", "mvar_psit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default);
# auto-/cross-effects are fixed across people.
sit_trend_mod$pars$indvarying <- sit_trend_mod$pars$param %in%
  c("T0m_pa_trend", "T0m_psit_trend", "cint_pa_trend", "cint_psit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects);
# not the trend drifts, trend T0MEANS/CINT, DIFFUSION or measurement part
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
sit_trend_mod$pars[, eff] <- FALSE
sit_trend_mod$pars[sit_trend_mod$pars$matrix == "DRIFT" &
               sit_trend_mod$pars$param %in% c("pa_pa", "psit_pa", "pa_psit", "psit_psit"), eff] <- TRUE

sit_trend_mod$pars[sit_trend_mod$pars$indvarying | rowSums(sit_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(sit_trend_mod)
```

### Fit Model
```{r}
#| eval: false
# ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
sit_trend_fit <- ctFit(
  datalong = sit_trend_data,
  model    = sit_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(sit_trend_fit, "02_files/sit_trend_fit.Rds")

```

```{r}
sit_trend_fit <- readRDS("02_files/sit_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
sit_trend_fit <- ctGenerateFromFit(sit_trend_fit, nsamples = 100)
pp_sit_trend <- ctPostPredPlots(sit_trend_fit)
saveRDS(pp_sit_trend, "02_files/pp_sit_trend.rds")
beepr::beep(8)
```

```{r}
pp_sit_trend <- readRDS("02_files/pp_sit_trend.rds")
pp_sit_trend$Density
pp_sit_trend$MeanTrajectory
pp_sit_trend$LaggedCovariance_esm_pa
pp_sit_trend$LaggedCovariance_esm24
pp_sit_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(sit_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_sit_trend <- ct_dpars_plot(sit_trend_fit,
  exclude  = c("pa_trend", "psit_trend"),   # dynamic processes only
  times    = seq(0, 8, 0.02),
  nsamples = 100)
saveRDS(dp_sit_trend, "02_files/dp_sit_trend.rds")
beepr::beep(8)
```

```{r}
dp_sit_trend <- readRDS("02_files/dp_sit_trend.rds")
dp_sit_trend$plot_auto
dp_sit_trend$plot_cross
dp_sit_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(sit_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_sit_trend <- ct_mod_grid(
  sit_trend_fit,
  latentNames = c("pa", "psit", "pa_trend", "psit_trend"),
  effects     = c("pa", "psit>pa", "pa>psit", "psit"),
  tipreds     = c("zpos", "zneg", "zdis"),
  labels      = c(zpos = "Positive Schizotypy", zneg = "Negative Schizotypy",
                  zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.04),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_sit_trend, "02_files/mod_sit_trend.rds")
beepr::beep(8)
```

##### ZPOS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_sit_trend <- readRDS("02_files/mod_sit_trend.rds")
patchwork::wrap_plots(lapply(mod_sit_trend$zpos, `[[`, "plot"), ncol = 2, guides = "collect")
```

## Stressful Situation (esm25)

### Model Specification
```{r}
# Per-model data: one row per id x time_day (no zero intervals) and drop
# beeps where both outcomes are missing (saves memory / time).
str_trend_data <- p2_data %>%
  group_by(id) %>% filter(!duplicated(time_day)) %>% ungroup() %>%
  filter(!(is.na(esm_pa) & is.na(esm25))) %>%
  mutate(across(c(esm_pa, esm25, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

str_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_pa", "esm25"),
  latentNames   = c("pa", "ssit", "pa_trend", "ssit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (ssit_pa = ssit -> pa);
  # trend factors only have their own (slow) drift, no cross-links
  DRIFT = matrix(c(
    "pa_pa",      "ssit_pa",      0,                0,
    "pa_ssit",    "ssit_ssit",    0,                0,
    0,            0,              "drift_pa_trend", 0,
    0,            0,              0,                "drift_ssit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only (trends are smooth)
  DIFFUSION = matrix(c(
    "diff_pa",      0,           0, 0,
    "diff_pa_ssit", "diff_ssit", 0, 0,
    0,              0,           0, 0,
    0,              0,           0, 0), 4, 4, byrow = TRUE),
  # T0VAR -- initial within-person deviations; trend starting points are
  # captured by the random T0MEANS instead
  T0VAR = matrix(c(
    "T0var_pa",      0,             0, 0,
    "T0var_pa_ssit", "T0var_ssit", 0, 0,
    0,               0,             0, 0,
    0,               0,             0, 0), 4, 4, byrow = TRUE),
  # Trend factors: person-specific starting level (T0MEANS) and
  # person-specific level the trend drifts toward (CINT)
  T0MEANS = c(0, 0, "T0m_pa_trend", "T0m_ssit_trend"),
  CINT    = c(0, 0, "cint_pa_trend", "cint_ssit_trend"),
  MANIFESTMEANS = 0,
  # MANIFESTVAR: measurement error incl. its covariance (same-beep response
  # style / shared occasion error). Without it the shock correlation goes to
  # ~.99 and the cross-effects compensate.
  MANIFESTVAR = matrix(c(
    "mvar_pa",      0,
    "mvar_pa_ssit", "mvar_ssit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default);
# auto-/cross-effects are fixed across people.
str_trend_mod$pars$indvarying <- str_trend_mod$pars$param %in%
  c("T0m_pa_trend", "T0m_ssit_trend", "cint_pa_trend", "cint_ssit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects);
# not the trend drifts, trend T0MEANS/CINT, DIFFUSION or measurement part
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
str_trend_mod$pars[, eff] <- FALSE
str_trend_mod$pars[str_trend_mod$pars$matrix == "DRIFT" &
               str_trend_mod$pars$param %in% c("pa_pa", "ssit_pa", "pa_ssit", "ssit_ssit"), eff] <- TRUE

str_trend_mod$pars[str_trend_mod$pars$indvarying | rowSums(str_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(str_trend_mod)
```

### Fit Model
```{r}
#| eval: false
# ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
str_trend_fit <- ctFit(
  datalong = str_trend_data,
  model    = str_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(str_trend_fit, "02_files/str_trend_fit.Rds")

```

```{r}
str_trend_fit <- readRDS("02_files/str_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
str_trend_fit <- ctGenerateFromFit(str_trend_fit, nsamples = 100)
pp_str_trend <- ctPostPredPlots(str_trend_fit)
saveRDS(pp_str_trend, "02_files/pp_str_trend.rds")
str_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_str_trend <- readRDS("02_files/pp_str_trend.rds")
pp_str_trend$Density
pp_str_trend$MeanTrajectory
pp_str_trend$LaggedCovariance_esm_pa
pp_str_trend$LaggedCovariance_esm25
pp_str_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(str_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_str_trend <- ct_dpars_plot(str_trend_fit,
  exclude  = c("pa_trend", "ssit_trend"),   # dynamic processes only
  times    = seq(0, 2, 0.02),
  nsamples = 100)
saveRDS(dp_str_trend, "02_files/dp_str_trend.rds")
beepr::beep(8)
```

```{r}
dp_str_trend <- readRDS("02_files/dp_str_trend.rds")
dp_str_trend$plot_auto
dp_str_trend$plot_cross
dp_str_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(str_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_str_trend <- ct_mod_grid(
  str_trend_fit,
  latentNames = c("ssit"),
  effects     = c("ssit"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_str_trend, "02_files/mod_str_trend.rds")
beepr::beep(8)
```
```{r}
mod_str_trend <- readRDS("02_files/mod_str_trend.rds")
```

##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
patchwork::wrap_plots(lapply(mod_str_trend$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```

```{r}
#| include: false
saveRDS(p2_data, "data/p2_data.Rds")
```

