---
title: "Psychotic-like Experiences"
format:
  html:
    toc: true
    toc-depth: 6
code-line-numbers: true
code-annotations: true
editor_options:
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
```

```{r}
#| include: false
p3_data <- readRDS("data/p2_data.Rds")
```

### Standardize Variables
```{r}
p3_data <- p3_data %>%
  mutate(across(c(esm_psx_con, zpos, zneg, zdis, esm_psx_sum), scale))

p3_data %>%
  select(esm_psx_sum, esm_psx_bin, esm_psx_con, zpos, zneg, zdis) %>%
  psych::describe()
```

### Julia Backend Setup
```{r}
library(ctsem)
ctJuliaSetup(threads = 10, force = TRUE)
JuliaConnectoR::juliaEval("ContinuousTimeSEM._CTSEM_COUNT_MAX_LOG_RATE[] = 15.0")
JuliaConnectoR::juliaEval("ContinuousTimeSEM._CTSEM_COUNT_GENERATE_MAX[] = 500")
```

## PSX Index (Censored)

### Model Specification
```{r}
psx_sum_ctsem <- "
# Measurement Model
psx_B =~ esm_psx_sum
psx_W =~ esm_psx_sum

# Between/Trend
psx_B  ~  psx_B
psx_B ~~  0*psx_B
psx_B %~% psx_B

# Within (dynamic) factor
psx_W  ~  psx_W
psx_W ~~  psx_W
psx_W %~% psx_W

## T0MEAN
psx_B ~t0~ 1

CENSOR: esm_psx_sum
"

psx_censored_syn <- ct_lavaan(psx_sum_ctsem, data = p3_data)

psx_censored_mod <- ctModel(
  type          = "ct",
  id            = "id",
  time          = "time_day",
  latentNames   = psx_censored_syn$latentNames,
  manifestNames = psx_censored_syn$manifestNames,
  LAMBDA        = psx_censored_syn$LAMBDA,
  DRIFT         = psx_censored_syn$DRIFT,
  DIFFUSION     = psx_censored_syn$DIFFUSION,
  T0VAR         = psx_censored_syn$T0VAR,
  CINT          = psx_censored_syn$CINT,
  T0MEANS       = psx_censored_syn$T0MEANS,
  MANIFESTMEANS = psx_censored_syn$MANIFESTMEANS,
  manifesttype  = psx_censored_syn$manifesttype,
  censormin     = psx_censored_syn$censormin,
  censormax     = psx_censored_syn$censormax,
  n.TIpred      = 3,
  TIpredNames   = c("zpos", "zneg", "zdis")
)

print(psx_censored_mod$pars[psx_censored_mod$pars$matrix == "DRIFT",
                             c("matrix", "row", "col",
                               "zpos_effect", "zneg_effect", "zdis_effect")])
```

### Fit Model
```{r}
#| eval: false
psx_censored_fit <- ctFit(
  datalong = p3_data,
  model    = psx_censored_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_censored_fit, "03_files/psx_censored_fit.Rds")
```

### Evaluate Model Fit
```{r}
psx_censored_fit <- readRDS("03_files/psx_censored_fit.Rds")
summary(psx_censored_fit)
```

#### Residual Auto-Correlation
```{r}
#| eval: false
acf_psx_censored_fit <- ctACFresiduals(
  psx_censored_fit,
  varnames = psx_censored_syn$manifestNames,
  nboot = 10
)
saveRDS(acf_psx_censored_fit, "03_files/acf_psx_censored.rds")
```

```{r}
acf_psx_censored_fit <- readRDS("03_files/acf_psx_censored.rds")
item_manifests <- psx_censored_syn$manifestNames
acf_psx_censored <- acf_psx_censored_fit$data

diag_dt_fit <- unique(
  acf_psx_censored[Variable %in% item_manifests,
                       .(TimeInterval, Variable, Q50 = `Q50%`, lo = `Q2.5%`, hi = `Q97.5%`, SignificanceLevel)]
)

ggplot(diag_dt_fit, aes(x = TimeInterval, y = Q50)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = .2) +
  geom_line() +
  geom_hline(aes(yintercept = SignificanceLevel), linetype = "dotted") +
  geom_hline(aes(yintercept = -SignificanceLevel), linetype = "dotted") +
  geom_hline(yintercept = 0, color = "grey50", linewidth = .3) +
  facet_wrap(~ Variable, ncol = 6, scales = "free_y") +
  labs(title = "Residual autocorrelation (PSX Index, censored)", y = "ACF", x = "Time interval (days)") +
  theme_minimal()
```

#### Posterior Predictive Check
```{r}
#| eval: false
pp_plot_psx_censored_fit <- ctPostPredPlots(psx_censored_fit)
saveRDS(pp_plot_psx_censored_fit, "03_files/pp_plot_psx_censored_fit.Rds")
save_postpred_plots(pp_plot_psx_censored_fit, "03_files/postpred_psx_censored")
```

```{r}
pp_plot_psx_censored_fit <- readRDS("03_files/pp_plot_psx_censored_fit.Rds")

for (panel_name in names(pp_plot_psx_censored_fit)) {
  cat("\n---", panel_name, "---\n")
  tryCatch(
    print(pp_plot_psx_censored_fit[[panel_name]]),
    error = function(e) {
      cat("  [", panel_name, "panel failed to render:", conditionMessage(e), "]\n")
    }
  )
}
```

### Visual
```{r}
set.seed(1111)
ct_effects_plot(
  psx_censored_fit,
  effects = c("psx_W>psx_W"),
  times = seq(0, 8, 0.01),
  ylim = c(0, 1),
  title = "Auto-effect: PSX Index (Censored)",
  legend_labels = c("PSX -> PSX"),
  latentNames = psx_censored_syn$latentNames
)
```

### Cross-level Interaction (+/- 1 SD)
```{r}
tip_names <- c("zpos", "zneg", "zdis")

for (nm in tip_names) {
  tipred_plots <- ctPredictTIP(
    psx_censored_fit,
    tipreds    = nm,
    doDynamics = TRUE,
    plot       = TRUE
  )

  print(
    tipred_plots$Process$Latent[[nm]] +
      ggplot2::labs(title = paste0("PSX Index (Censored): latent trajectories by ", nm, " (-1 SD / median / +1 SD)"))
  )
  print(
    tipred_plots$Dynamics$Independent[[nm]] +
      ggplot2::labs(title = paste0("PSX Index (Censored): dynamics (impulse response) by ", nm, " (-1 SD / median / +1 SD)"))
  )
}
```

## Two-Part Approach (Censored Magnitude)

### Model Specification
```{r}
psx_twopart_ctsem <- "
# Measurement Model
## BINARY
bin_psx_B =~ esm_psx_bin
bin_psx_W =~ esm_psx_bin

## CONT.
con_psx_B =~ esm_psx_con
con_psx_W =~ esm_psx_con

# Between/Trend
bin_psx_B  ~  bin_psx_B
bin_psx_B ~~  0*bin_psx_B
bin_psx_B %~% bin_psx_B

con_psx_B  ~  con_psx_B
con_psx_B ~~  0*con_psx_B
con_psx_B %~% con_psx_B

bin_psx_B %~% con_psx_B

# Within (dynamic) factor
## BINARY
bin_psx_W  ~  bin_psx_W
bin_psx_W ~~  bin_psx_W
bin_psx_W %~% bin_psx_W

## CONT.
con_psx_W  ~  con_psx_W
con_psx_W ~~  con_psx_W
con_psx_W %~% con_psx_W

## T0MEAN
bin_psx_B ~t0~ 1
con_psx_B ~t0~ 1

BINARY: esm_psx_bin
CENSOR: esm_psx_con
"

psx_twopart_syn <- ct_lavaan(psx_twopart_ctsem, data = p3_data)

psx_twopart_mod <- ctModel(
  type          = "ct",
  id            = "id",
  time          = "time_day",
  latentNames   = psx_twopart_syn$latentNames,
  manifestNames = psx_twopart_syn$manifestNames,
  LAMBDA        = psx_twopart_syn$LAMBDA,
  DRIFT         = psx_twopart_syn$DRIFT,
  DIFFUSION     = psx_twopart_syn$DIFFUSION,
  T0VAR         = psx_twopart_syn$T0VAR,
  CINT          = psx_twopart_syn$CINT,
  T0MEANS       = psx_twopart_syn$T0MEANS,
  MANIFESTMEANS = psx_twopart_syn$MANIFESTMEANS,
  manifesttype  = psx_twopart_syn$manifesttype,
  censormin     = psx_twopart_syn$censormin,
  censormax     = psx_twopart_syn$censormax,
  n.TIpred      = 3,
  TIpredNames   = c("zpos", "zneg", "zdis")
)

effect_cols <- c("zpos_effect", "zneg_effect", "zdis_effect")

con_w_idx <- match("con_psx_W", psx_twopart_syn$latentNames)
target_con <- psx_twopart_mod$pars$matrix == "DRIFT" &
              as.character(psx_twopart_mod$pars$row) == as.character(con_w_idx) &
              as.character(psx_twopart_mod$pars$col) == as.character(con_w_idx)

psx_twopart_mod$pars[target_con, effect_cols] <- FALSE

print(psx_twopart_mod$pars[psx_twopart_mod$pars$matrix == "DRIFT",
                            c("matrix", "row", "col", effect_cols)])
```

### Fit Model
```{r}
#| eval: false
psx_twopart_fit <- ctFit(
  datalong = p3_data,
  model    = psx_twopart_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_twopart_fit, "03_files/psx_twopart_fit.Rds")
```

### Evaluate Model Fit
```{r}
psx_twopart_fit <- readRDS("03_files/psx_twopart_fit.Rds")
summary(psx_twopart_fit)
```

#### Residual Auto-Correlation
```{r}
#| eval: false
acf_psx_twopart_fit <- ctACFresiduals(
  psx_twopart_fit,
  varnames = psx_twopart_syn$manifestNames,
  nboot = 10
)
saveRDS(acf_psx_twopart_fit, "03_files/acf_psx_twopart.rds")
```

```{r}
acf_psx_twopart_fit <- readRDS("03_files/acf_psx_twopart.rds")
item_manifests <- psx_twopart_syn$manifestNames
acf_psx_twopart <- acf_psx_twopart_fit$data

diag_dt_fit <- unique(
  acf_psx_twopart[Variable %in% item_manifests,
                       .(TimeInterval, Variable, Q50 = `Q50%`, lo = `Q2.5%`, hi = `Q97.5%`, SignificanceLevel)]
)

ggplot(diag_dt_fit, aes(x = TimeInterval, y = Q50)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = .2) +
  geom_line() +
  geom_hline(aes(yintercept = SignificanceLevel), linetype = "dotted") +
  geom_hline(aes(yintercept = -SignificanceLevel), linetype = "dotted") +
  geom_hline(yintercept = 0, color = "grey50", linewidth = .3) +
  facet_wrap(~ Variable, ncol = 6, scales = "free_y") +
  labs(title = "Residual autocorrelation (Two-Part, censored magnitude)", y = "ACF", x = "Time interval (days)") +
  theme_minimal()
```

#### Posterior Predictive Check
```{r}
#| eval: false
pp_plot_psx_twopart_fit <- ctPostPredPlots(psx_twopart_fit)
saveRDS(pp_plot_psx_twopart_fit, "03_files/pp_plot_psx_twopart_fit.Rds")
save_postpred_plots(pp_plot_psx_twopart_fit, "03_files/postpred_psx_twopart")
```

```{r}
pp_plot_psx_twopart_fit <- readRDS("03_files/pp_plot_psx_twopart_fit.Rds")

for (panel_name in names(pp_plot_psx_twopart_fit)) {
  cat("\n---", panel_name, "---\n")
  tryCatch(
    print(pp_plot_psx_twopart_fit[[panel_name]]),
    error = function(e) {
      cat("  [", panel_name, "panel failed to render:", conditionMessage(e), "]\n")
    }
  )
}
```

### Visual
#### Binary
```{r}
set.seed(1111)
ct_effects_plot(
  psx_twopart_fit,
  effects = c("bin_psx_W>bin_psx_W"),
  times = seq(0, 8, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Two-Part (Censored Magnitude)",
  legend_labels = c("PSX (occurrence) -> PSX (occurrence)"),
  latentNames = psx_twopart_syn$latentNames
)
```

#### Magnitude
```{r}
set.seed(1111)
ct_effects_plot(
  psx_twopart_fit,
  effects = c("con_psx_W>con_psx_W"),
  times = seq(0, 8, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Two-Part (Censored Magnitude)",
  legend_labels = c("PSX (magnitude) -> PSX (magnitude)"),
  latentNames = psx_twopart_syn$latentNames
)
```

### Cross-level Interaction (+/- 1 SD)
```{r}
tip_names <- c("zpos", "zneg", "zdis")

for (nm in tip_names) {
  tipred_plots <- ctPredictTIP(
    psx_twopart_fit,
    tipreds    = nm,
    doDynamics = TRUE,
    plot       = TRUE
  )

  print(
    tipred_plots$Process$Latent[[nm]] +
      ggplot2::labs(title = paste0("Latent trajectories by ", nm, " (-1 SD / median / +1 SD)"))
  )
  print(
    tipred_plots$Dynamics$Independent[[nm]] +
      ggplot2::labs(title = paste0("Dynamics (impulse response) by ", nm, " (-1 SD / median / +1 SD)"))
  )
}
```

```{r}
#| include: false
saveRDS(p3_data, "data/p3_data.Rds")
```
