---
title: "Psychotic-like Experiences"
format:
  html:
    toc: true
    toc-depth: 6
    lightbox: auto   # click any figure to enlarge / zoom
code-line-numbers: true
code-annotations: true
editor_options:
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Fugeomibbonnctions
```{r}
# remotes::install_github("cdriveraus/ctsem", ref = "juliaFit", force = T)
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/ct_halflife.R")
source("cust_funcs/mod_plot.R")
source("cust_funcs/ct_dpars_plot.R")
source("cust_funcs/ct_mod_grid.R")
source("cust_funcs/ct_sig_table.R")
source("cust_funcs/ct_tp_ppc.R")
```

```{r}
#| include: false
p3_data <- readRDS("data/p2_data.Rds")
```

### Standardize Variables
```{r}
p3_data <- p3_data %>%
  mutate(across(c(zpos, zneg, zdis, esm_psx_sum, esm24, esm25), scale))

p3_data %>%
  select(esm_psx_sum, esm_psx_bin, esm_psx_con, zpos, zneg, zdis) %>%
  psych::describe()
```

## CENSOR-AUTO

### Model Specification
```{r}
psx_cens_trend_data <- p3_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_sum, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

psx_cens_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_sum"),
  latentNames   = c("psx", "psx_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4),   # 0 continuous, 1 binary, 4 censored
  censormin     = c(min(psx_cens_trend_data$esm_psx_sum, na.rm = TRUE)),
  censormax     = c(Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(1), diag(1)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "psx_psx"        , 0,
    0                , "drift_psx_trend"),
    2, 2, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_psx", 0,
    0         , 0),
    2, 2, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_psx", 0,
    0          , 0),
    2, 2, byrow = TRUE),
  T0MEANS = c(0, "T0m_psx_trend"),
  CINT    = c(0, "cint_psx_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_psx"),
    1, 1, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
psx_cens_trend_mod$pars$indvarying <- psx_cens_trend_mod$pars$param %in% c("T0m_psx_trend", "cint_psx_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_cens_trend_mod$pars[, eff] <- FALSE
psx_cens_trend_mod$pars[psx_cens_trend_mod$pars$matrix == "DRIFT" &
               psx_cens_trend_mod$pars$param %in% c("psx_psx"), eff] <- TRUE

psx_cens_trend_mod$pars[psx_cens_trend_mod$pars$indvarying | rowSums(psx_cens_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_cens_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_cens_trend_fit <- ctFit(
  datalong = psx_cens_trend_data,
  model    = psx_cens_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_cens_trend_fit, "03_files/psx_cens_trend_fit.Rds")
beepr::beep(8)
```

```{r}
psx_cens_trend_fit <- readRDS("03_files/psx_cens_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
psx_cens_trend_fit <- ctGenerateFromFit(psx_cens_trend_fit, nsamples = 100)
pp_psx_cens_trend <- ctPostPredPlots(psx_cens_trend_fit)
saveRDS(pp_psx_cens_trend, "03_files/pp_psx_cens_trend.rds")
psx_cens_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_cens_trend <- readRDS("03_files/pp_psx_cens_trend.rds")
pp_psx_cens_trend$Density
pp_psx_cens_trend$MeanTrajectory
pp_psx_cens_trend$LaggedCovariance_esm_psx_sum
pp_psx_cens_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(psx_cens_trend_fit)
```

### Half-Life
```{r}
ct_halflife(psx_cens_trend_fit, c("psx", "psx_trend"), pattern = NULL) %>%
  ct_sig_gt(lower = "drift_2.5", upper = "drift_97.5")
```

### Auto-Effects
```{r}
#| eval: false
set.seed(1111)
dp_psx_cens_trend <- ct_dpars_plot(psx_cens_trend_fit,
  type     = "auto",   # auto-effects only (no cross-effects in this model)
  exclude  = c("psx_trend"),   # dynamic process(es) only
  times    = seq(0, 2, 0.02),
  nsamples = 100)
saveRDS(dp_psx_cens_trend, "03_files/dp_psx_cens_trend.rds")
beepr::beep(8)
```

```{r}
dp_psx_cens_trend <- readRDS("03_files/dp_psx_cens_trend.rds")
dp_psx_cens_trend$plot_auto
```

### Moderation
#### TIpred Effects
```{r}
summary(psx_cens_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_psx_cens_trend <- ct_mod_grid(
  psx_cens_trend_fit,
  latentNames = c("psx", "psx_trend"),
  effects     = c("psx"),
  tipreds     = c("zpos", "zneg", "zdis"),
  labels      = c(zpos = "Positive Schizotypy", zneg = "Negative Schizotypy",
                  zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.04),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_psx_cens_trend, "03_files/mod_psx_cens_trend.rds")
beepr::beep(8)
```

##### ZPOS
```{r}
#| fig-width: 6
#| fig-height: 4
mod_psx_cens_trend <- readRDS("03_files/mod_psx_cens_trend.rds")
patchwork::wrap_plots(lapply(mod_psx_cens_trend$zpos, `[[`, "plot"), ncol = 1, guides = "collect")
```

##### ZNEG
```{r}
#| fig-width: 6
#| fig-height: 4
patchwork::wrap_plots(lapply(mod_psx_cens_trend$zneg, `[[`, "plot"), ncol = 1, guides = "collect")
```

##### ZDIS
```{r}
#| fig-width: 6
#| fig-height: 4
patchwork::wrap_plots(lapply(mod_psx_cens_trend$zdis, `[[`, "plot"), ncol = 1, guides = "collect")
```

## CENSOR-PSIT

### Model Specification
```{r}
psx_sit_trend_data <- p3_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_sum, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

psx_sit_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_sum", "esm24"),
  latentNames   = c("psx", "psit", "psx_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4, 0),                                  # censored, continuous
  censormin     = c(min(psx_sit_trend_data$esm_psx_sum, na.rm = TRUE), -Inf), # floor of esm_psx_sum
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (psit_psx = psit -> psx)
  DRIFT = matrix(c(
    "psx_psx"         , "psit_psx"        , 0                 , 0                 ,
    "psx_psit"        , "psit_psit"       , 0                 , 0                 ,
    0                 , 0                 , "drift_psx_trend" , 0                 ,
    0                 , 0                 , 0                 , "drift_psit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_psx"     , 0              , 0              , 0              ,
    "diff_psx_psit", "diff_psit"    , 0              , 0              ,
    0              , 0              , 0              , 0              ,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_psx"     , 0               , 0               , 0               ,
    "T0var_psx_psit", "T0var_psit"    , 0               , 0               ,
    0               , 0               , 0               , 0               ,
    0               , 0               , 0               , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_psx_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, "cint_psx_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_psx", 0,
    0,          "mvar_psit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
psx_sit_trend_mod$pars$indvarying <- psx_sit_trend_mod$pars$param %in%
  c("T0m_psx_trend", "T0m_psit_trend", "cint_psx_trend", "cint_psit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_sit_trend_mod$pars[, eff] <- FALSE
psx_sit_trend_mod$pars[psx_sit_trend_mod$pars$matrix == "DRIFT" &
               psx_sit_trend_mod$pars$param %in% c("psx_psx", "psit_psx", "psx_psit", "psit_psit"), eff] <- TRUE

psx_sit_trend_mod$pars[psx_sit_trend_mod$pars$indvarying | rowSums(psx_sit_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_sit_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_sit_trend_fit <- ctFit(
  datalong = psx_sit_trend_data,
  model    = psx_sit_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_sit_trend_fit, "03_files/psx_sit_trend_fit.Rds")
beepr::beep(8)
```

```{r}
psx_sit_trend_fit <- readRDS("03_files/psx_sit_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
psx_sit_trend_fit <- ctGenerateFromFit(psx_sit_trend_fit, nsamples = 100)
pp_psx_sit_trend <- ctPostPredPlots(psx_sit_trend_fit)
saveRDS(pp_psx_sit_trend, "03_files/pp_psx_sit_trend.rds")
psx_sit_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_sit_trend <- readRDS("03_files/pp_psx_sit_trend.rds")
pp_psx_sit_trend$Density
pp_psx_sit_trend$MeanTrajectory
pp_psx_sit_trend$LaggedCovariance_esm_psx_sum
pp_psx_sit_trend$LaggedCovariance_esm24
pp_psx_sit_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(psx_sit_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_psx_sit_trend <- ct_dpars_plot(psx_sit_trend_fit,
  exclude  = c("psx_trend", "psit_trend"),   # dynamic processes only
  times    = seq(0, 2, 0.02),
  nsamples = 100)
saveRDS(dp_psx_sit_trend, "03_files/dp_psx_sit_trend.rds")
beepr::beep(8)
```

```{r}
dp_psx_sit_trend <- readRDS("03_files/dp_psx_sit_trend.rds")
dp_psx_sit_trend$plot_auto
dp_psx_sit_trend$plot_cross
dp_psx_sit_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(psx_sit_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_psx_sit_trend <- ct_mod_grid(
  psx_sit_trend_fit,
  latentNames = c("psx", "psit", "psx_trend", "psit_trend"),
  effects     = c("psx", "psit>psx", "psx>psit", "psit"),
  tipreds     = c("zpos", "zneg", "zdis"),
  labels      = c(zpos = "Positive Schizotypy", zneg = "Negative Schizotypy",
                  zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.04),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_psx_sit_trend, "03_files/mod_psx_sit_trend.rds")
beepr::beep(8)
```

##### ZPOS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_psx_sit_trend <- readRDS("03_files/mod_psx_sit_trend.rds")
patchwork::wrap_plots(lapply(mod_psx_sit_trend$zpos, `[[`, "plot"), ncol = 2, guides = "collect")
```

##### ZNEG
```{r}
#| fig-width: 12
#| fig-height: 8
patchwork::wrap_plots(lapply(mod_psx_sit_trend$zneg, `[[`, "plot"), ncol = 2, guides = "collect")
```

##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
patchwork::wrap_plots(lapply(mod_psx_sit_trend$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```

## CENSOR-SSIT

### Model Specification
```{r}
psx_str_trend_data <- p3_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_sum, esm25, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

psx_str_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_sum", "esm25"),
  latentNames   = c("psx", "ssit", "psx_trend", "ssit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4, 0),                                  # censored, continuous
  censormin     = c(min(psx_str_trend_data$esm_psx_sum, na.rm = TRUE), -Inf), # floor of esm_psx_sum
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (ssit_psx = ssit -> psx)
  DRIFT = matrix(c(
    "psx_psx"         , "ssit_psx"        , 0                 , 0                 ,
    "psx_ssit"        , "ssit_ssit"       , 0                 , 0                 ,
    0                 , 0                 , "drift_psx_trend" , 0                 ,
    0                 , 0                 , 0                 , "drift_ssit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_psx"     , 0              , 0              , 0              ,
    "diff_psx_ssit", "diff_ssit"    , 0              , 0              ,
    0              , 0              , 0              , 0              ,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_psx"     , 0               , 0               , 0               ,
    "T0var_psx_ssit", "T0var_ssit"    , 0               , 0               ,
    0               , 0               , 0               , 0               ,
    0               , 0               , 0               , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_psx_trend", "T0m_ssit_trend"),
  CINT    = c(0, 0, "cint_psx_trend", "cint_ssit_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_psx", 0,
    0,          "mvar_ssit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
psx_str_trend_mod$pars$indvarying <- psx_str_trend_mod$pars$param %in%
  c("T0m_psx_trend", "T0m_ssit_trend", "cint_psx_trend", "cint_ssit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_str_trend_mod$pars[, eff] <- FALSE
psx_str_trend_mod$pars[psx_str_trend_mod$pars$matrix == "DRIFT" &
               psx_str_trend_mod$pars$param %in% c("psx_psx", "ssit_psx", "psx_ssit", "ssit_ssit"), eff] <- TRUE

psx_str_trend_mod$pars[psx_str_trend_mod$pars$indvarying | rowSums(psx_str_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_str_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_str_trend_fit <- ctFit(
  datalong = psx_str_trend_data,
  model    = psx_str_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_str_trend_fit, "03_files/psx_str_trend_fit.Rds")
beepr::beep(8)
```

```{r}
psx_str_trend_fit <- readRDS("03_files/psx_str_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
psx_str_trend_fit <- ctGenerateFromFit(psx_str_trend_fit, nsamples = 100)
pp_psx_str_trend <- ctPostPredPlots(psx_str_trend_fit)
saveRDS(pp_psx_str_trend, "03_files/pp_psx_str_trend.rds")
psx_str_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_str_trend <- readRDS("03_files/pp_psx_str_trend.rds")
pp_psx_str_trend$Density
pp_psx_str_trend$MeanTrajectory
pp_psx_str_trend$LaggedCovariance_esm_psx_sum
pp_psx_str_trend$LaggedCovariance_esm25
pp_psx_str_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(psx_str_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_psx_str_trend <- ct_dpars_plot(psx_str_trend_fit,
  exclude  = c("psx_trend", "ssit_trend"),   # dynamic processes only
  times    = seq(0, 2, 0.02),
  nsamples = 100)
saveRDS(dp_psx_str_trend, "03_files/dp_psx_str_trend.rds")
beepr::beep(8)
```

```{r}
dp_psx_str_trend <- readRDS("03_files/dp_psx_str_trend.rds")
dp_psx_str_trend$plot_auto
dp_psx_str_trend$plot_cross
dp_psx_str_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(psx_str_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_psx_str_trend_neg <- ct_mod_grid(
  psx_str_trend_fit,
  latentNames = c("psx", "ssit"),
  effects     = c("psx", "ssit>psx", "psx>ssit", "ssit"),
  tipreds     = c("zneg"),
  labels      = c(zneg = "Negative Schizotypy"),
  times       = seq(0, 5, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_psx_str_trend_neg, "03_files/mod_psx_str_trend_neg.rds")
beepr::beep(8)
```

##### ZNEG
```{r}
#| fig-width: 12
#| fig-height: 8
mod_psx_str_trend_neg <- readRDS("03_files/mod_psx_str_trend_neg.rds")
patchwork::wrap_plots(lapply(mod_psx_str_trend_neg$zneg, `[[`, "plot"), ncol = 2, guides = "collect")
```

##### ZDIS
```{r}
#| eval: false
set.seed(1111)
mod_psx_str_trend_dis <- ct_mod_grid(
  psx_str_trend_fit,
  latentNames = c("psx", "ssit"),
  effects     = c("psx", "psx>ssit"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, 5, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_psx_str_trend_dis, "03_files/mod_psx_str_trend_dis.rds")
beepr::beep(8)
```
```{r}
#| fig-width: 12
#| fig-height: 8
mod_psx_str_trend_dis <- readRDS("03_files/mod_psx_str_trend_dis.rds")
patchwork::wrap_plots(lapply(mod_psx_str_trend_dis$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```

## Sensitivity Checks

:::callout-note
Non-final models, kept for comparison (specification, fit, posterior predictive check and results table).

- **TP-ORD-LINK-AUTO**: two-part (occurrence + ordinal magnitude) with the occurrence-magnitude link.
- **TP-ORD-AUTO / TP-CENS-AUTO / TP-CNT-AUTO**: two-part without the link; ordinal, censored and count magnitude.
- **TP-AUTO-EVER**: TP-ORD-LINK-AUTO without the participants who never reported any occurrence.
- **TP-PSIT / TP-SSIT**: two-part (occurrence + censored magnitude) versions of CENSOR-PSIT / CENSOR-SSIT.
- **TP-ORD-PSIT / TP-ORD-SSIT**: TP-PSIT / TP-SSIT with ordinal magnitude.
:::

### TP-ORD-LINK-AUTO

#### Model Specification
```{r}
# ordinal magnitude from the raw (unscaled) esm_psx_con: 9 categories
raw_con <- as.numeric(readRDS("data/p2_data.Rds")$esm_psx_con)
stopifnot(length(raw_con) == nrow(p3_data), all(raw_con[!is.na(raw_con)] >= 1))
ord_breaks <- c(0, 1, 2, 3, 4, 5, 6, 9, 12, Inf)   # 1,2,3,4,5,6,7-9,10-12,13+

psx_tpo2_data <- p3_data %>%
  mutate(esm_psx_ord = as.numeric(cut(raw_con, breaks = ord_breaks, labels = FALSE))) %>%  # 1..9, NA when absent
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_ord, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

table(psx_tpo2_data$esm_psx_ord, useNA = "ifany")   # 460 232 253 194 187 139 172 119 181 + NA

psx_tpo2_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_ord"),
  latentNames   = c("bin_psx", "ord_psx", "bin_psx_trend", "ord_psx_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 2),   # binary, ordinal
  ncategories   = c(0, 9),   # 9 ordinal categories for esm_psx_ord
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , 0                    , 0,
    0                    , "ord_psx_ord_psx"    , 0                    , 0,
    0                    , 0                    , "drift_bin_psx_trend", 0,
    0                    , 0                    , 0                    , "drift_ord_psx_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_bin_psx"    , 0                 , 0                 , 0,
    "diff_bin_ord_psx", "diff_ord_psx"    , 0                 , 0,
    0                 , 0                 , 0                 , 0,
    0                 , 0                 , 0                 , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx"    , 0                  , 0                  , 0,
    "T0var_bin_ord_psx", "T0var_ord_psx"    , 0                  , 0,
    0                  , 0                  , 0                  , 0,
    0                  , 0                  , 0                  , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_bin_psx_trend", "T0m_ord_psx_trend"),
  CINT    = c(0, 0, "cint_bin_psx_trend", "cint_ord_psx_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    0             , 0,
    0             , 0),
    2, 2, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
psx_tpo2_mod$pars$indvarying <- psx_tpo2_mod$pars$param %in% c("T0m_bin_psx_trend", "T0m_ord_psx_trend", "cint_bin_psx_trend", "cint_ord_psx_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_tpo2_mod$pars[, eff] <- FALSE
psx_tpo2_mod$pars[psx_tpo2_mod$pars$matrix == "DRIFT" &
               psx_tpo2_mod$pars$param %in% c("bin_psx_bin_psx", "ord_psx_ord_psx"), eff] <- TRUE

psx_tpo2_mod$pars[psx_tpo2_mod$pars$indvarying | rowSums(psx_tpo2_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_tpo2_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_tpo2_fit <- ctFit(
  datalong = psx_tpo2_data,
  model    = psx_tpo2_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_tpo2_fit, "03_files/psx_tpo2_fit.Rds")
beepr::beep(8)
```

```{r}
psx_tpo2_fit <- readRDS("03_files/psx_tpo2_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_tpo2_fit <- ctGenerateFromFit(psx_tpo2_fit, nsamples = 100)
pp_psx_tpo2 <- ctPostPredPlots(psx_tpo2_fit)
saveRDS(pp_psx_tpo2, "03_files/pp_psx_tpo2.rds")

# two-part check: magnitude only where the MODEL's own occurrence = 1
tpc_psx_tpo2 <- ct_tp_ppc(psx_tpo2_fit, psx_tpo2_data, "esm_psx_bin", "esm_psx_ord",
  breaks = NULL)
saveRDS(tpc_psx_tpo2, "03_files/tpc_psx_tpo2.rds")
psx_tpo2_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_tpo2 <- readRDS("03_files/pp_psx_tpo2.rds")
pp_psx_tpo2$Density
pp_psx_tpo2$MeanTrajectory
pp_psx_tpo2$LaggedCovariance_esm_psx_bin
pp_psx_tpo2$LaggedCovariance_esm_psx_ord
pp_psx_tpo2$SubjectLogLik
```

#### Results Table
```{r}
ct_sig_table(psx_tpo2_fit)
```

### TP-ORD-AUTO

#### Model Specification
```{r}
# ordinal magnitude from the raw (unscaled) esm_psx_con: 9 categories
raw_con <- as.numeric(readRDS("data/p2_data.Rds")$esm_psx_con)
stopifnot(length(raw_con) == nrow(p3_data), all(raw_con[!is.na(raw_con)] >= 1))
ord_breaks <- c(0, 1, 2, 3, 4, 5, 6, 9, 12, Inf)   # 1,2,3,4,5,6,7-9,10-12,13+

psx_tpo_trend_data <- p3_data %>%
  mutate(esm_psx_ord = as.numeric(cut(raw_con, breaks = ord_breaks, labels = FALSE))) %>%  # 1..9, NA when absent
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_ord, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

table(psx_tpo_trend_data$esm_psx_ord, useNA = "ifany")   # expect 460 232 253 194 187 139 172 119 181 + NA

psx_tpo_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_ord"),
  latentNames   = c("bin_psx", "ord_psx", "bin_psx_trend", "ord_psx_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 2),   # binary, ordinal
  ncategories   = c(0, 9),   # 9 ordinal categories for esm_psx_ord
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , 0                    , 0,
    0                    , "ord_psx_ord_psx"    , 0                    , 0,
    0                    , 0                    , "drift_bin_psx_trend", 0,
    0                    , 0                    , 0                    , "drift_ord_psx_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_bin_psx", 0             , 0             , 0,
    0             , "diff_ord_psx", 0             , 0,
    0             , 0             , 0             , 0,
    0             , 0             , 0             , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx", 0              , 0              , 0,
    0              , "T0var_ord_psx", 0              , 0,
    0              , 0              , 0              , 0,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_bin_psx_trend", "T0m_ord_psx_trend"),
  CINT    = c(0, 0, "cint_bin_psx_trend", "cint_ord_psx_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    0             , 0,
    0             , 0),
    2, 2, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
psx_tpo_trend_mod$pars$indvarying <- psx_tpo_trend_mod$pars$param %in% c("T0m_bin_psx_trend", "T0m_ord_psx_trend", "cint_bin_psx_trend", "cint_ord_psx_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_tpo_trend_mod$pars[, eff] <- FALSE
psx_tpo_trend_mod$pars[psx_tpo_trend_mod$pars$matrix == "DRIFT" &
               psx_tpo_trend_mod$pars$param %in% c("bin_psx_bin_psx", "ord_psx_ord_psx"), eff] <- TRUE

psx_tpo_trend_mod$pars[psx_tpo_trend_mod$pars$indvarying | rowSums(psx_tpo_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_tpo_trend_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine: outcome type changed to ordinal
psx_tpo_trend_fit <- ctFit(
  datalong = psx_tpo_trend_data,
  model    = psx_tpo_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_tpo_trend_fit, "03_files/psx_tpo_trend_fit.Rds")
beepr::beep(8)
```

```{r}
psx_tpo_trend_fit <- readRDS("03_files/psx_tpo_trend_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_tpo_trend_fit <- ctGenerateFromFit(psx_tpo_trend_fit, nsamples = 100)
pp_psx_tpo_trend <- ctPostPredPlots(psx_tpo_trend_fit)
saveRDS(pp_psx_tpo_trend, "03_files/pp_psx_tpo_trend.rds")

# observed vs model category proportions. Two-part PPC: a simulated magnitude
# only counts where the MODEL's own occurrence is 1 (ctPostPredPlots instead
# uses the observed occurrence pattern, which biases magnitude low).
Y <- psx_tpo_trend_fit$generated$Y
stopifnot(dim(Y)[2] == nrow(psx_tpo_trend_data))
g_bin <- Y[, , "esm_psx_bin"]
g_mag <- Y[, , "esm_psx_ord"]; g_mag[g_bin == 0] <- NA
o_bin <- psx_tpo_trend_data$esm_psx_bin
o_mag <- psx_tpo_trend_data$esm_psx_ord
ptab <- function(o, g, v) full_join(
  as.data.frame(prop.table(table(category = o)), responseName = "observed"),
  as.data.frame(prop.table(table(category = round(g))), responseName = "model"),
  by = "category") %>% mutate(variable = v, .before = 1)
prop_psx_tpo_trend <- bind_rows(
  ptab(o_bin, g_bin[, !is.na(o_bin)], "esm_psx_bin"),
  ptab(o_mag, g_mag, "esm_psx_ord (given occurrence)"))
# mean magnitude by day, same conditioning
day <- floor(psx_tpo_trend_data$time_day)
mean_psx_tpo_trend <- tibble(day = day, observed = o_mag,
                     model = colMeans(g_mag, na.rm = TRUE)) %>%
  group_by(day) %>%
  summarise(observed = mean(observed, na.rm = TRUE), model = mean(model, na.rm = TRUE))
saveRDS(mean_psx_tpo_trend, "03_files/mean_psx_tpo_trend.rds")
saveRDS(prop_psx_tpo_trend, "03_files/prop_psx_tpo_trend.rds")
rm(Y); psx_tpo_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_tpo_trend <- readRDS("03_files/pp_psx_tpo_trend.rds")
pp_psx_tpo_trend$Density
pp_psx_tpo_trend$MeanTrajectory
pp_psx_tpo_trend$LaggedCovariance_esm_psx_bin
pp_psx_tpo_trend$LaggedCovariance_esm_psx_ord
pp_psx_tpo_trend$SubjectLogLik
```

##### Observed vs Model Proportions
```{r}
readRDS("03_files/prop_psx_tpo_trend.rds") %>%
  gt::gt(groupname_col = "variable") %>%
  gt::fmt_percent(columns = c(observed, model), decimals = 1)
```

```{r}
readRDS("03_files/mean_psx_tpo_trend.rds") %>%
  pivot_longer(-day, names_to = "source", values_to = "mean") %>%
  ggplot(aes(day, mean, colour = source)) + geom_line() + geom_point() +
  labs(x = "Study day", y = "Mean magnitude category (given occurrence)", colour = NULL) +
  theme_bw()
```

### TP-CENS-AUTO

#### Model Specification
```{r}
psx_tp_trend_data <- p3_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_con, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

psx_tp_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_con"),
  latentNames   = c("bin_psx", "con_psx", "bin_psx_trend", "con_psx_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 4),   # 0 continuous, 1 binary, 4 censored
  censormin     = c(-Inf, min(psx_tp_trend_data$esm_psx_con, na.rm = TRUE)),
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , 0                    , 0,
    0                    , "con_psx_con_psx"    , 0                    , 0,
    0                    , 0                    , "drift_bin_psx_trend", 0,
    0                    , 0                    , 0                    , "drift_con_psx_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_bin_psx", 0             , 0             , 0,
    0             , "diff_con_psx", 0             , 0,
    0             , 0             , 0             , 0,
    0             , 0             , 0             , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx", 0              , 0              , 0,
    0              , "T0var_con_psx", 0              , 0,
    0              , 0              , 0              , 0,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_bin_psx_trend", "T0m_con_psx_trend"),
  CINT    = c(0, 0, "cint_bin_psx_trend", "cint_con_psx_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    0             , 0,
    0             , "mvar_con_psx"),
    2, 2, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
psx_tp_trend_mod$pars$indvarying <- psx_tp_trend_mod$pars$param %in% c("T0m_bin_psx_trend", "T0m_con_psx_trend", "cint_bin_psx_trend", "cint_con_psx_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_tp_trend_mod$pars[, eff] <- FALSE
psx_tp_trend_mod$pars[psx_tp_trend_mod$pars$matrix == "DRIFT" &
               psx_tp_trend_mod$pars$param %in% c("bin_psx_bin_psx", "con_psx_con_psx"), eff] <- TRUE

psx_tp_trend_mod$pars[psx_tp_trend_mod$pars$indvarying | rowSums(psx_tp_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_tp_trend_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_tp_trend_fit <- ctFit(
  datalong = psx_tp_trend_data,
  model    = psx_tp_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_tp_trend_fit, "03_files/psx_tp_trend_fit.Rds")
beepr::beep(8)
```

```{r}
psx_tp_trend_fit <- readRDS("03_files/psx_tp_trend_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_tp_trend_fit <- ctGenerateFromFit(psx_tp_trend_fit, nsamples = 100)
pp_psx_tp_trend <- ctPostPredPlots(psx_tp_trend_fit)
saveRDS(pp_psx_tp_trend, "03_files/pp_psx_tp_trend.rds")
psx_tp_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_tp_trend <- readRDS("03_files/pp_psx_tp_trend.rds")
pp_psx_tp_trend$Density
pp_psx_tp_trend$MeanTrajectory
pp_psx_tp_trend$LaggedCovariance_esm_psx_bin
pp_psx_tp_trend$LaggedCovariance_esm_psx_con
pp_psx_tp_trend$SubjectLogLik
```

### TP-CNT-AUTO

#### Model Specification
```{r}
# count = raw (unscaled) magnitude - 1; the Standardize chunk may have
# z-scored esm_psx_con, so take it from the saved data (same rows as p3_data)
raw_con <- as.numeric(readRDS("data/p2_data.Rds")$esm_psx_con)
stopifnot(length(raw_con) == nrow(p3_data),
          all(raw_con[!is.na(raw_con)] >= 1),
          all(raw_con[!is.na(raw_con)] == round(raw_con[!is.na(raw_con)])))  # whole numbers >= 1

psx_tpc_trend_data <- p3_data %>%
  mutate(esm_psx_cnt = raw_con - 1) %>%   # 0, 1, 2, ... ; NA when absent
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_cnt, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

psx_tpc_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_cnt"),
  latentNames   = c("bin_psx", "cnt_psx", "bin_psx_trend", "cnt_psx_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 3),   # binary, count (Poisson-lognormal)
  # (censormin/censormax not needed: no censored variables here)
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , 0                    , 0,
    0                    , "cnt_psx_cnt_psx"    , 0                    , 0,
    0                    , 0                    , "drift_bin_psx_trend", 0,
    0                    , 0                    , 0                    , "drift_cnt_psx_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_bin_psx", 0             , 0             , 0,
    0             , "diff_cnt_psx", 0             , 0,
    0             , 0             , 0             , 0,
    0             , 0             , 0             , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx", 0              , 0              , 0,
    0              , "T0var_cnt_psx", 0              , 0,
    0              , 0              , 0              , 0,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_bin_psx_trend", "T0m_cnt_psx_trend"),
  CINT    = c(0, 0, "cint_bin_psx_trend", "cint_cnt_psx_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    0             , 0,
    0             , "mvar_cnt_psx"),
    2, 2, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
psx_tpc_trend_mod$pars$indvarying <- psx_tpc_trend_mod$pars$param %in% c("T0m_bin_psx_trend", "T0m_cnt_psx_trend", "cint_bin_psx_trend", "cint_cnt_psx_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_tpc_trend_mod$pars[, eff] <- FALSE
psx_tpc_trend_mod$pars[psx_tpc_trend_mod$pars$matrix == "DRIFT" &
               psx_tpc_trend_mod$pars$param %in% c("bin_psx_bin_psx", "cnt_psx_cnt_psx"), eff] <- TRUE

psx_tpc_trend_mod$pars[psx_tpc_trend_mod$pars$indvarying | rowSums(psx_tpc_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_tpc_trend_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine: outcome type changed to count
psx_tpc_trend_fit <- ctFit(
  datalong = psx_tpc_trend_data,
  model    = psx_tpc_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_tpc_trend_fit, "03_files/psx_tpc_trend_fit.Rds")
beepr::beep(8)
```

```{r}
psx_tpc_trend_fit <- readRDS("03_files/psx_tpc_trend_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_tpc_trend_fit <- ctGenerateFromFit(psx_tpc_trend_fit, nsamples = 100)
pp_psx_tpc_trend <- ctPostPredPlots(psx_tpc_trend_fit)
saveRDS(pp_psx_tpc_trend, "03_files/pp_psx_tpc_trend.rds")
psx_tpc_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_tpc_trend <- readRDS("03_files/pp_psx_tpc_trend.rds")
pp_psx_tpc_trend$Density
pp_psx_tpc_trend$MeanTrajectory
pp_psx_tpc_trend$LaggedCovariance_esm_psx_bin
pp_psx_tpc_trend$LaggedCovariance_esm_psx_cnt
pp_psx_tpc_trend$SubjectLogLik
```

### TP-AUTO-EVER

:::callout-note
TP-ORD-LINK-AUTO refitted without the participants who never reported PSX (37 of 203). Those
participants produce the step at the right end of TP-AUTO's `SubjectLogLik` plot; if the
dynamics and moderation effects barely change without them, they are not driving the results.
:::

#### Fit Model
```{r}
#| eval: false
ever_ids <- psx_tpo2_data %>% group_by(id) %>%
  filter(any(esm_psx_bin == 1, na.rm = TRUE)) %>% pull(id) %>% unique()
psx_tpo2_ever_data <- psx_tpo2_data %>% filter(id %in% ever_ids)

psx_tpo2_ever_fit <- ctFit(
  datalong = psx_tpo2_ever_data,
  model    = psx_tpo2_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_tpo2_ever_fit, "03_files/psx_tpo2_ever_fit.Rds")
beepr::beep(8)

psx_tpo2_ever_fit <- ctGenerateFromFit(psx_tpo2_ever_fit, nsamples = 100)
pp_psx_tpo2_ever <- ctPostPredPlots(psx_tpo2_ever_fit)
saveRDS(pp_psx_tpo2_ever, "03_files/pp_psx_tpo2_ever.rds")
psx_tpo2_ever_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
psx_tpo2_ever_fit <- readRDS("03_files/psx_tpo2_ever_fit.Rds")
pp_psx_tpo2_ever  <- readRDS("03_files/pp_psx_tpo2_ever.rds")
pp_psx_tpo2_ever$SubjectLogLik
```

#### Comparison with TP-ORD-LINK-AUTO
```{r}
cmp_pars <- function(fit) {
  s <- summary(fit)
  keep <- c("mean", "2.5%", "97.5%")
  rbind(as.data.frame(s$popmeans)[, keep], as.data.frame(s$tipreds)[, keep]) %>%
    tibble::rownames_to_column("param")
}
full_join(cmp_pars(psx_tpo2_fit), cmp_pars(psx_tpo2_ever_fit),
          by = "param", suffix = c("_all", "_ever")) %>%
  filter(grepl("_psx_|^tip_", param)) %>%
  gt::gt() %>%
  gt::fmt_number(columns = -param, decimals = 3)
```

### TP-PSIT

#### Model Specification
```{r}
psx_sit_tp_data <- p3_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_con, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

table(psx_sit_tp_data$esm_psx_bin, useNA = "ifany")   # binary part must be 0/1

psx_sit_tp_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_con", "esm24"),
  latentNames   = c("bin_psx", "con_psx", "psit", "bin_psx_trend", "con_psx_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 4, 0),                        # binary, censored, continuous
  censormin     = c(-Inf, min(psx_sit_tp_data$esm_psx_con, na.rm = TRUE), -Inf),
  censormax     = c(Inf, Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(3), diag(3)),
  # DRIFT -- labels are predictor_outcome (psit_bin_psx = psit -> bin_psx)
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , "psit_bin_psx"       , 0                    , 0                    , 0                    ,
    0                    , "con_psx_con_psx"    , "psit_con_psx"       , 0                    , 0                    , 0                    ,
    "bin_psx_psit"       , "con_psx_psit"       , "psit_psit"          , 0                    , 0                    , 0                    ,
    0                    , 0                    , 0                    , "drift_bin_psx_trend", 0                    , 0                    ,
    0                    , 0                    , 0                    , 0                    , "drift_con_psx_trend", 0                    ,
    0                    , 0                    , 0                    , 0                    , 0                    , "drift_psit_trend"),
    6, 6, byrow = TRUE),
  # DIFFUSION -- system noise (full covariance) on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_bin_psx"        , 0                     , 0                     , 0                     , 0                     , 0                     ,
    "diff_bin_psx_con_psx", "diff_con_psx"        , 0                     , 0                     , 0                     , 0                     ,
    "diff_bin_psx_psit"   , "diff_con_psx_psit"   , "diff_psit"           , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0),
    6, 6, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx"        , 0                      , 0                      , 0                      , 0                      , 0                      ,
    "T0var_bin_psx_con_psx", "T0var_con_psx"        , 0                      , 0                      , 0                      , 0                      ,
    "T0var_bin_psx_psit"   , "T0var_con_psx_psit"   , "T0var_psit"           , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0),
    6, 6, byrow = TRUE),
  T0MEANS = c(0, 0, 0, "T0m_bin_psx_trend", "T0m_con_psx_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, 0, "cint_bin_psx_trend", "cint_con_psx_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  # binary part: no measurement error (the link carries it)
  MANIFESTVAR = matrix(c(
    0, 0,          0,
    0, "mvar_con_psx", 0,
    0, 0,          "mvar_psit"), 3, 3, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
psx_sit_tp_mod$pars$indvarying <- psx_sit_tp_mod$pars$param %in%
  c("T0m_bin_psx_trend", "T0m_con_psx_trend", "T0m_psit_trend",
    "cint_bin_psx_trend", "cint_con_psx_trend", "cint_psit_trend")

# TIpreds moderate the seven dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_sit_tp_mod$pars[, eff] <- FALSE
psx_sit_tp_mod$pars[psx_sit_tp_mod$pars$matrix == "DRIFT" &
               psx_sit_tp_mod$pars$param %in% c("bin_psx_bin_psx", "con_psx_con_psx", "psit_psit", "psit_bin_psx", "psit_con_psx", "bin_psx_psit", "con_psx_psit"), eff] <- TRUE

psx_sit_tp_mod$pars[psx_sit_tp_mod$pars$indvarying | rowSums(psx_sit_tp_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_sit_tp_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_sit_tp_fit <- ctFit(
  datalong = psx_sit_tp_data,
  model    = psx_sit_tp_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_sit_tp_fit, "03_files/psx_sit_tp_fit.Rds")
beepr::beep(8)
```

```{r}
psx_sit_tp_fit <- readRDS("03_files/psx_sit_tp_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_sit_tp_fit <- ctGenerateFromFit(psx_sit_tp_fit, nsamples = 100)
pp_psx_sit_tp <- ctPostPredPlots(psx_sit_tp_fit)
saveRDS(pp_psx_sit_tp, "03_files/pp_psx_sit_tp.rds")

# two-part check: magnitude only where the MODEL's own occurrence = 1
tpc_psx_sit_tp <- ct_tp_ppc(psx_sit_tp_fit, psx_sit_tp_data, "esm_psx_bin", "esm_psx_con",
  breaks = c(-Inf, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 9.5, 12.5, Inf),
  labels = c("1", "2", "3", "4", "5", "6", "7-9", "10-12", "13+"))
saveRDS(tpc_psx_sit_tp, "03_files/tpc_psx_sit_tp.rds")
psx_sit_tp_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_sit_tp <- readRDS("03_files/pp_psx_sit_tp.rds")
pp_psx_sit_tp$Density
pp_psx_sit_tp$MeanTrajectory
pp_psx_sit_tp$LaggedCovariance_esm_psx_bin
pp_psx_sit_tp$LaggedCovariance_esm_psx_con
pp_psx_sit_tp$LaggedCovariance_esm24
pp_psx_sit_tp$SubjectLogLik
```

#### Results Table
```{r}
ct_sig_table(psx_sit_tp_fit)
```

### TP-ORD-PSIT

#### Model Specification
```{r}
# ordinal magnitude from the raw (unscaled) esm_psx_con: 9 categories
raw_con <- as.numeric(readRDS("data/p2_data.Rds")$esm_psx_con)
stopifnot(length(raw_con) == nrow(p3_data), all(raw_con[!is.na(raw_con)] >= 1))
ord_breaks <- c(0, 1, 2, 3, 4, 5, 6, 9, 12, Inf)   # 1,2,3,4,5,6,7-9,10-12,13+

psx_sit_tpo_data <- p3_data %>%
  mutate(esm_psx_ord = as.numeric(cut(raw_con, breaks = ord_breaks, labels = FALSE))) %>%  # 1..9, NA when absent
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_ord, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

table(psx_sit_tpo_data$esm_psx_bin, useNA = "ifany")   # binary part must be 0/1

psx_sit_tpo_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_ord", "esm24"),
  latentNames   = c("bin_psx", "ord_psx", "psit", "bin_psx_trend", "ord_psx_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 2, 0),   # binary, ordinal, continuous
  ncategories   = c(0, 9, 0),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(3), diag(3)),
  # DRIFT -- labels are predictor_outcome (psit_bin_psx = psit -> bin_psx)
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , "psit_bin_psx"       , 0                    , 0                    , 0                    ,
    0                    , "ord_psx_ord_psx"    , "psit_ord_psx"       , 0                    , 0                    , 0                    ,
    "bin_psx_psit"       , "ord_psx_psit"       , "psit_psit"          , 0                    , 0                    , 0                    ,
    0                    , 0                    , 0                    , "drift_bin_psx_trend", 0                    , 0                    ,
    0                    , 0                    , 0                    , 0                    , "drift_ord_psx_trend", 0                    ,
    0                    , 0                    , 0                    , 0                    , 0                    , "drift_psit_trend"),
    6, 6, byrow = TRUE),
  # DIFFUSION -- system noise (full covariance) on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_bin_psx"        , 0                     , 0                     , 0                     , 0                     , 0                     ,
    "diff_bin_psx_ord_psx", "diff_ord_psx"        , 0                     , 0                     , 0                     , 0                     ,
    "diff_bin_psx_psit"   , "diff_ord_psx_psit"   , "diff_psit"           , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0),
    6, 6, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx"        , 0                      , 0                      , 0                      , 0                      , 0                      ,
    "T0var_bin_psx_ord_psx", "T0var_ord_psx"        , 0                      , 0                      , 0                      , 0                      ,
    "T0var_bin_psx_psit"   , "T0var_ord_psx_psit"   , "T0var_psit"           , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0),
    6, 6, byrow = TRUE),
  T0MEANS = c(0, 0, 0, "T0m_bin_psx_trend", "T0m_ord_psx_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, 0, "cint_bin_psx_trend", "cint_ord_psx_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  # binary + ordinal parts: no measurement error (the links carry it)
  MANIFESTVAR = matrix(c(
    0, 0,          0,
    0, 0,          0,
    0, 0,          "mvar_psit"), 3, 3, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
psx_sit_tpo_mod$pars$indvarying <- psx_sit_tpo_mod$pars$param %in%
  c("T0m_bin_psx_trend", "T0m_ord_psx_trend", "T0m_psit_trend",
    "cint_bin_psx_trend", "cint_ord_psx_trend", "cint_psit_trend")

# TIpreds moderate the seven dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_sit_tpo_mod$pars[, eff] <- FALSE
psx_sit_tpo_mod$pars[psx_sit_tpo_mod$pars$matrix == "DRIFT" &
               psx_sit_tpo_mod$pars$param %in% c("bin_psx_bin_psx", "ord_psx_ord_psx", "psit_psit", "psit_bin_psx", "psit_ord_psx", "bin_psx_psit", "ord_psx_psit"), eff] <- TRUE

psx_sit_tpo_mod$pars[psx_sit_tpo_mod$pars$indvarying | rowSums(psx_sit_tpo_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_sit_tpo_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_sit_tpo_fit <- ctFit(
  datalong = psx_sit_tpo_data,
  model    = psx_sit_tpo_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_sit_tpo_fit, "03_files/psx_sit_tpo_fit.Rds")
beepr::beep(8)
```

```{r}
psx_sit_tpo_fit <- readRDS("03_files/psx_sit_tpo_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_sit_tpo_fit <- ctGenerateFromFit(psx_sit_tpo_fit, nsamples = 100)
pp_psx_sit_tpo <- ctPostPredPlots(psx_sit_tpo_fit)
saveRDS(pp_psx_sit_tpo, "03_files/pp_psx_sit_tpo.rds")

# two-part check: magnitude only where the MODEL's own occurrence = 1
tpc_psx_sit_tpo <- ct_tp_ppc(psx_sit_tpo_fit, psx_sit_tpo_data, "esm_psx_bin", "esm_psx_ord",
  breaks = NULL)
saveRDS(tpc_psx_sit_tpo, "03_files/tpc_psx_sit_tpo.rds")
psx_sit_tpo_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_sit_tpo <- readRDS("03_files/pp_psx_sit_tpo.rds")
pp_psx_sit_tpo$Density
pp_psx_sit_tpo$MeanTrajectory
pp_psx_sit_tpo$LaggedCovariance_esm_psx_bin
pp_psx_sit_tpo$LaggedCovariance_esm_psx_ord
pp_psx_sit_tpo$LaggedCovariance_esm24
pp_psx_sit_tpo$SubjectLogLik
```

##### Two-Part Check
```{r}
tpc_psx_sit_tpo <- readRDS("03_files/tpc_psx_sit_tpo.rds")
tpc_psx_sit_tpo$prop %>%
  gt::gt(groupname_col = "variable") %>%
  gt::fmt_percent(columns = c(observed, model), decimals = 1)
tpc_psx_sit_tpo$plot
```

#### Results Table
```{r}
ct_sig_table(psx_sit_tpo_fit)
```

### TP-SSIT

#### Model Specification
```{r}
psx_str_tp_data <- p3_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_psx_bin, esm_psx_con, esm25, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

table(psx_str_tp_data$esm_psx_bin, useNA = "ifany")   # binary part must be 0/1

psx_str_tp_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_psx_bin", "esm_psx_con", "esm25"),
  latentNames   = c("bin_psx", "con_psx", "ssit", "bin_psx_trend", "con_psx_trend", "ssit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(1, 4, 0),                        # binary, censored, continuous
  censormin     = c(-Inf, min(psx_str_tp_data$esm_psx_con, na.rm = TRUE), -Inf),
  censormax     = c(Inf, Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(3), diag(3)),
  # DRIFT -- labels are predictor_outcome (ssit_bin_psx = ssit -> bin_psx)
  DRIFT = matrix(c(
    "bin_psx_bin_psx"    , 0                    , "ssit_bin_psx"       , 0                    , 0                    , 0                    ,
    0                    , "con_psx_con_psx"    , "ssit_con_psx"       , 0                    , 0                    , 0                    ,
    "bin_psx_ssit"       , "con_psx_ssit"       , "ssit_ssit"          , 0                    , 0                    , 0                    ,
    0                    , 0                    , 0                    , "drift_bin_psx_trend", 0                    , 0                    ,
    0                    , 0                    , 0                    , 0                    , "drift_con_psx_trend", 0                    ,
    0                    , 0                    , 0                    , 0                    , 0                    , "drift_ssit_trend"),
    6, 6, byrow = TRUE),
  # DIFFUSION -- system noise (full covariance) on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_bin_psx"        , 0                     , 0                     , 0                     , 0                     , 0                     ,
    "diff_bin_psx_con_psx", "diff_con_psx"        , 0                     , 0                     , 0                     , 0                     ,
    "diff_bin_psx_ssit"   , "diff_con_psx_ssit"   , "diff_ssit"           , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0                     ,
    0                     , 0                     , 0                     , 0                     , 0                     , 0),
    6, 6, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_bin_psx"        , 0                      , 0                      , 0                      , 0                      , 0                      ,
    "T0var_bin_psx_con_psx", "T0var_con_psx"        , 0                      , 0                      , 0                      , 0                      ,
    "T0var_bin_psx_ssit"   , "T0var_con_psx_ssit"   , "T0var_ssit"           , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0                      ,
    0                      , 0                      , 0                      , 0                      , 0                      , 0),
    6, 6, byrow = TRUE),
  T0MEANS = c(0, 0, 0, "T0m_bin_psx_trend", "T0m_con_psx_trend", "T0m_ssit_trend"),
  CINT    = c(0, 0, 0, "cint_bin_psx_trend", "cint_con_psx_trend", "cint_ssit_trend"),
  MANIFESTMEANS = 0,
  # binary part: no measurement error (the link carries it)
  MANIFESTVAR = matrix(c(
    0, 0,          0,
    0, "mvar_con_psx", 0,
    0, 0,          "mvar_ssit"), 3, 3, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
psx_str_tp_mod$pars$indvarying <- psx_str_tp_mod$pars$param %in%
  c("T0m_bin_psx_trend", "T0m_con_psx_trend", "T0m_ssit_trend",
    "cint_bin_psx_trend", "cint_con_psx_trend", "cint_ssit_trend")

# TIpreds moderate the seven dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
psx_str_tp_mod$pars[, eff] <- FALSE
psx_str_tp_mod$pars[psx_str_tp_mod$pars$matrix == "DRIFT" &
               psx_str_tp_mod$pars$param %in% c("bin_psx_bin_psx", "con_psx_con_psx", "ssit_ssit", "ssit_bin_psx", "ssit_con_psx", "bin_psx_ssit", "con_psx_ssit"), eff] <- TRUE

psx_str_tp_mod$pars[psx_str_tp_mod$pars$indvarying | rowSums(psx_str_tp_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(psx_str_tp_mod)
```

#### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
psx_str_tp_fit <- ctFit(
  datalong = psx_str_tp_data,
  model    = psx_str_tp_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(psx_str_tp_fit, "03_files/psx_str_tp_fit.Rds")
beepr::beep(8)
```

```{r}
psx_str_tp_fit <- readRDS("03_files/psx_str_tp_fit.Rds")
```

#### Posterior Predictive Check
```{r}
#| eval: false
psx_str_tp_fit <- ctGenerateFromFit(psx_str_tp_fit, nsamples = 100)
pp_psx_str_tp <- ctPostPredPlots(psx_str_tp_fit)
saveRDS(pp_psx_str_tp, "03_files/pp_psx_str_tp.rds")

# two-part check: magnitude only where the MODEL's own occurrence = 1
tpc_psx_str_tp <- ct_tp_ppc(psx_str_tp_fit, psx_str_tp_data, "esm_psx_bin", "esm_psx_con",
  breaks = c(-Inf, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 9.5, 12.5, Inf),
  labels = c("1", "2", "3", "4", "5", "6", "7-9", "10-12", "13+"))
saveRDS(tpc_psx_str_tp, "03_files/tpc_psx_str_tp.rds")
psx_str_tp_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_psx_str_tp <- readRDS("03_files/pp_psx_str_tp.rds")
pp_psx_str_tp$Density
pp_psx_str_tp$MeanTrajectory
pp_psx_str_tp$LaggedCovariance_esm_psx_bin
pp_psx_str_tp$LaggedCovariance_esm_psx_con
pp_psx_str_tp$LaggedCovariance_esm25
pp_psx_str_tp$SubjectLogLik
```

#### Results Table
```{r}
ct_sig_table(psx_str_tp_fit)
```
