---
title: "Negative Affect"
format:
  html:
    toc: true
    toc-depth: 6
    lightbox: auto   # click any figure to enlarge / zoom
code-line-numbers: true
code-annotations: true
editor_options:
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/ct_halflife.R")
source("cust_funcs/mod_plot.R")
source("cust_funcs/ct_dpars_plot.R")
source("cust_funcs/ct_mod_grid.R")
source("cust_funcs/ct_sig_table.R")
```

```{r}
#| include: false
p4_data <- readRDS("data/p2_data.Rds")
```

### Standardize Variables
```{r}
p4_data <- p4_data %>%
  mutate(across(c(esm_na, esm_na_con, zpos, zneg, zdis, esm24, esm25), scale))

p4_data %>%
  select(esm_na, esm_na_bin, esm_na_con, zpos, zneg, zdis) %>%
  psych::describe()
```

## CENSOR-AUTO

### Model Specification
```{r}
na_cens_trend_data <- p4_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_na, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

na_cens_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_na"),
  latentNames   = c("na", "na_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4),   # 0 continuous, 1 binary, 4 censored
  censormin     = c(min(na_cens_trend_data$esm_na, na.rm = TRUE)),
  censormax     = c(Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(1), diag(1)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "na_na"         , 0,
    0               , "drift_na_trend"),
    2, 2, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_na", 0,
    0        , 0),
    2, 2, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_na", 0,
    0         , 0),
    2, 2, byrow = TRUE),
  T0MEANS = c(0, "T0m_na_trend"),
  CINT    = c(0, "cint_na_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_na"),
    1, 1, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
na_cens_trend_mod$pars$indvarying <- na_cens_trend_mod$pars$param %in% c("T0m_na_trend", "cint_na_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
na_cens_trend_mod$pars[, eff] <- FALSE
na_cens_trend_mod$pars[na_cens_trend_mod$pars$matrix == "DRIFT" &
               na_cens_trend_mod$pars$param %in% c("na_na"), eff] <- TRUE

na_cens_trend_mod$pars[na_cens_trend_mod$pars$indvarying | rowSums(na_cens_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(na_cens_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
na_cens_trend_fit <- ctFit(
  datalong = na_cens_trend_data,
  model    = na_cens_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(na_cens_trend_fit, "04_files/na_cens_trend_fit.Rds")
beepr::beep(8)
```

```{r}
na_cens_trend_fit <- readRDS("04_files/na_cens_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
na_cens_trend_fit <- ctGenerateFromFit(na_cens_trend_fit, nsamples = 100)
pp_na_cens_trend <- ctPostPredPlots(na_cens_trend_fit)
saveRDS(pp_na_cens_trend, "04_files/pp_na_cens_trend.rds")
na_cens_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_na_cens_trend <- readRDS("04_files/pp_na_cens_trend.rds")
pp_na_cens_trend$Density
pp_na_cens_trend$MeanTrajectory
pp_na_cens_trend$LaggedCovariance_esm_na
pp_na_cens_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(na_cens_trend_fit)
```

### Half-Life
```{r}
ct_halflife(na_cens_trend_fit, c("na", "na_trend"), pattern = NULL) %>%
  ct_sig_gt(lower = "drift_2.5", upper = "drift_97.5")
```

### Auto-Effects
```{r}
#| eval: false
set.seed(1111)
dp_na_cens_trend <- ct_dpars_plot(na_cens_trend_fit,
  type     = "auto",   # auto-effects only (no cross-effects in this model)
  exclude  = c("na_trend"),   # dynamic process(es) only
  times    = seq(0, 2, 0.01),
  nsamples = 100, standardise = TRUE)
saveRDS(dp_na_cens_trend, "04_files/dp_na_cens_trend.rds")
beepr::beep(8)
```

```{r}
dp_na_cens_trend <- readRDS("04_files/dp_na_cens_trend.rds")
dp_na_cens_trend$plot_auto
```

### Moderation
#### TIpred Effects
```{r}
summary(na_cens_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

## CENSOR-PSIT

### Model Specification
```{r}
na_sit_trend_data <- p4_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_na, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

na_sit_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_na", "esm24"),
  latentNames   = c("na", "psit", "na_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4, 0),                                  # censored, continuous
  censormin     = c(min(na_sit_trend_data$esm_na, na.rm = TRUE), -Inf), # floor of esm_na
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (psit_na = psit -> na)
  DRIFT = matrix(c(
    "na_na"           , "psit_na"         , 0                 , 0                 ,
    "na_psit"         , "psit_psit"       , 0                 , 0                 ,
    0                 , 0                 , "drift_na_trend"  , 0                 ,
    0                 , 0                 , 0                 , "drift_psit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only (correlation fixed to 0)
  DIFFUSION = matrix(c(
    "diff_na"     , 0             , 0             , 0             ,
    0, "diff_psit"   , 0             , 0             ,
    0             , 0             , 0             , 0             ,
    0             , 0             , 0             , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_na"     , 0              , 0              , 0              ,
    "T0var_na_psit", "T0var_psit"   , 0              , 0              ,
    0              , 0              , 0              , 0              ,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_na_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, "cint_na_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  # MANIFESTVAR: occasion-specific error variances + covariance
  # (same-moment association is carried here; DIFFUSION correlation fixed to 0)
  MANIFESTVAR = matrix(c(
    "mvar_na",      0,
    "mvar_na_psit", "mvar_psit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
na_sit_trend_mod$pars$indvarying <- na_sit_trend_mod$pars$param %in%
  c("T0m_na_trend", "T0m_psit_trend", "cint_na_trend", "cint_psit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
na_sit_trend_mod$pars[, eff] <- FALSE
na_sit_trend_mod$pars[na_sit_trend_mod$pars$matrix == "DRIFT" &
               na_sit_trend_mod$pars$param %in% c("na_na", "psit_na", "na_psit", "psit_psit"), eff] <- TRUE

na_sit_trend_mod$pars[na_sit_trend_mod$pars$indvarying | rowSums(na_sit_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(na_sit_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
na_sit_trend_fit <- ctFit(
  datalong = na_sit_trend_data,
  model    = na_sit_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(na_sit_trend_fit, "04_files/na_sit_trend_fit.Rds")
beepr::beep(8)
```

```{r}
na_sit_trend_fit <- readRDS("04_files/na_sit_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
na_sit_trend_fit <- ctGenerateFromFit(na_sit_trend_fit, nsamples = 100)
pp_na_sit_trend <- ctPostPredPlots(na_sit_trend_fit)
saveRDS(pp_na_sit_trend, "04_files/pp_na_sit_trend.rds")
na_sit_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_na_sit_trend <- readRDS("04_files/pp_na_sit_trend.rds")
pp_na_sit_trend$Density
pp_na_sit_trend$MeanTrajectory
pp_na_sit_trend$LaggedCovariance_esm_na
pp_na_sit_trend$LaggedCovariance_esm24
pp_na_sit_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(na_sit_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_na_sit_trend <- ct_dpars_plot(na_sit_trend_fit,
  exclude  = c("na_trend", "psit_trend"),   # dynamic processes only
  times    = seq(0, .5, 0.001),
  nsamples = 100,
  standardise = TRUE)
saveRDS(dp_na_sit_trend, "04_files/dp_na_sit_trend.rds")
beepr::beep(8)
```

```{r}
dp_na_sit_trend <- readRDS("04_files/dp_na_sit_trend.rds")
dp_na_sit_trend$plot_auto
dp_na_sit_trend$plot_cross
dp_na_sit_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(na_sit_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

## CENSOR-SSIT

### Model Specification
```{r}
na_str_trend_data <- p4_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_na, esm25, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

na_str_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_na", "esm25"),
  latentNames   = c("na", "ssit", "na_trend", "ssit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4, 0),                                  # censored, continuous
  censormin     = c(min(na_str_trend_data$esm_na, na.rm = TRUE), -Inf), # floor of esm_na
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (ssit_na = ssit -> na)
  DRIFT = matrix(c(
    "na_na"           , "ssit_na"         , 0                 , 0                 ,
    "na_ssit"         , "ssit_ssit"       , 0                 , 0                 ,
    0                 , 0                 , "drift_na_trend"  , 0                 ,
    0                 , 0                 , 0                 , "drift_ssit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only (correlation fixed to 0)
  DIFFUSION = matrix(c(
    "diff_na"     , 0             , 0             , 0             ,
    0, "diff_ssit"   , 0             , 0             ,
    0             , 0             , 0             , 0             ,
    0             , 0             , 0             , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_na"     , 0              , 0              , 0              ,
    "T0var_na_ssit", "T0var_ssit"   , 0              , 0              ,
    0              , 0              , 0              , 0              ,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_na_trend", "T0m_ssit_trend"),
  CINT    = c(0, 0, "cint_na_trend", "cint_ssit_trend"),
  MANIFESTMEANS = 0,
  # MANIFESTVAR: occasion-specific error variances + covariance
  # (same-moment association is carried here; DIFFUSION correlation fixed to 0)
  MANIFESTVAR = matrix(c(
    "mvar_na",      0,
    "mvar_na_ssit", "mvar_ssit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
na_str_trend_mod$pars$indvarying <- na_str_trend_mod$pars$param %in%
  c("T0m_na_trend", "T0m_ssit_trend", "cint_na_trend", "cint_ssit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
na_str_trend_mod$pars[, eff] <- FALSE
na_str_trend_mod$pars[na_str_trend_mod$pars$matrix == "DRIFT" &
               na_str_trend_mod$pars$param %in% c("na_na", "ssit_na", "na_ssit", "ssit_ssit"), eff] <- TRUE

na_str_trend_mod$pars[na_str_trend_mod$pars$indvarying | rowSums(na_str_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(na_str_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
na_str_trend_fit <- ctFit(
  datalong = na_str_trend_data,
  model    = na_str_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(na_str_trend_fit, "04_files/na_str_trend_fit.Rds")
beepr::beep(8)
```

```{r}
na_str_trend_fit <- readRDS("04_files/na_str_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
na_str_trend_fit <- ctGenerateFromFit(na_str_trend_fit, nsamples = 100)
pp_na_str_trend <- ctPostPredPlots(na_str_trend_fit)
saveRDS(pp_na_str_trend, "04_files/pp_na_str_trend.rds")
na_str_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_na_str_trend <- readRDS("04_files/pp_na_str_trend.rds")
pp_na_str_trend$Density
pp_na_str_trend$MeanTrajectory
pp_na_str_trend$LaggedCovariance_esm_na
pp_na_str_trend$LaggedCovariance_esm25
pp_na_str_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(na_str_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_na_str_trend <- ct_dpars_plot(na_str_trend_fit,
  exclude  = c("na_trend", "ssit_trend"),   # dynamic processes only
  times    = seq(0, .5, 0.001),
  nsamples = 150,
  standardise = TRUE)
saveRDS(dp_na_str_trend, "04_files/dp_na_str_trend.rds")
beepr::beep(8)
```

```{r}
dp_na_str_trend <- readRDS("04_files/dp_na_str_trend.rds")
dp_na_str_trend$plot_auto
dp_na_str_trend$plot_cross
dp_na_str_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(na_str_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_na_str_trend <- ct_mod_grid(
  na_str_trend_fit,
  latentNames = c("na", "ssit"),
  effects     = c("ssit>na", "ssit"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, .5, 0.001),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_na_str_trend, "04_files/mod_na_str_trend.rds")
beepr::beep(8)
```

```{r}
mod_na_str_trend <- readRDS("04_files/mod_na_str_trend.rds")
```

##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_na_str_trend <- readRDS("04_files/mod_na_str_trend.rds")
patchwork::wrap_plots(lapply(mod_na_str_trend$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```
