---
title: "Disorganized Experiences"
format:
  html:
    toc: true
    toc-depth: 6
    lightbox: auto   # click any figure to enlarge / zoom
code-line-numbers: true
code-annotations: true
editor_options:
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/ct_halflife.R")
source("cust_funcs/mod_plot.R")
source("cust_funcs/ct_dpars_plot.R")
source("cust_funcs/ct_mod_grid.R")
source("cust_funcs/ct_sig_table.R")
```

```{r}
#| include: false
p5_data <- readRDS("data/p2_data.Rds")
```

### Standardize Variables
```{r}
p5_data <- p5_data %>%
  mutate(across(c(esm_dis, esm_dis_con, zpos, zneg, zdis, esm24, esm25), scale))

p5_data %>%
  select(esm_dis, esm_dis_bin, esm_dis_con, zpos, zneg, zdis) %>%
  psych::describe()
```

## CENSOR-AUTO

### Model Specification
```{r}
dis_cens_trend_data <- p5_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_dis, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

dis_cens_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_dis"),
  latentNames   = c("dis", "dis_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4),   # 0 continuous, 1 binary, 4 censored
  censormin     = c(min(dis_cens_trend_data$esm_dis, na.rm = TRUE)),
  censormax     = c(Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(1), diag(1)),
  # DRIFT -- dynamic auto-effects + slow trend drifts
  DRIFT = matrix(c(
    "dis_dis"        , 0,
    0                , "drift_dis_trend"),
    2, 2, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic process(es) only
  DIFFUSION = matrix(c(
    "diff_dis", 0,
    0         , 0),
    2, 2, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_dis", 0,
    0          , 0),
    2, 2, byrow = TRUE),
  T0MEANS = c(0, "T0m_dis_trend"),
  CINT    = c(0, "cint_dis_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_dis"),
    1, 1, byrow = TRUE)
)

# Random effects = the trend factor's T0MEANS and CINT only (EAS default)
dis_cens_trend_mod$pars$indvarying <- dis_cens_trend_mod$pars$param %in% c("T0m_dis_trend", "cint_dis_trend")

# TIpreds moderate the dynamic auto-effect(s) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
dis_cens_trend_mod$pars[, eff] <- FALSE
dis_cens_trend_mod$pars[dis_cens_trend_mod$pars$matrix == "DRIFT" &
               dis_cens_trend_mod$pars$param %in% c("dis_dis"), eff] <- TRUE

dis_cens_trend_mod$pars[dis_cens_trend_mod$pars$indvarying | rowSums(dis_cens_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(dis_cens_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
dis_cens_trend_fit <- ctFit(
  datalong = dis_cens_trend_data,
  model    = dis_cens_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(dis_cens_trend_fit, "05_files/dis_cens_trend_fit.Rds")
beepr::beep(8)
```

```{r}
dis_cens_trend_fit <- readRDS("05_files/dis_cens_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
dis_cens_trend_fit <- ctGenerateFromFit(dis_cens_trend_fit, nsamples = 100)
pp_dis_cens_trend <- ctPostPredPlots(dis_cens_trend_fit)
saveRDS(pp_dis_cens_trend, "05_files/pp_dis_cens_trend.rds")
dis_cens_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_dis_cens_trend <- readRDS("05_files/pp_dis_cens_trend.rds")
pp_dis_cens_trend$Density
pp_dis_cens_trend$MeanTrajectory
pp_dis_cens_trend$LaggedCovariance_esm_dis
pp_dis_cens_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(dis_cens_trend_fit)
```

### Half-Life
```{r}
ct_halflife(dis_cens_trend_fit, c("dis", "dis_trend"), pattern = NULL) %>%
  ct_sig_gt(lower = "drift_2.5", upper = "drift_97.5")
```

### Auto-Effects
```{r}
#| eval: false
set.seed(1111)
dp_dis_cens_trend <- ct_dpars_plot(dis_cens_trend_fit,
  type     = "auto",   # auto-effects only (no cross-effects in this model)
  exclude  = c("dis_trend"),   # dynamic process(es) only
  times    = seq(0, 2, 0.01),
  nsamples = 100)
saveRDS(dp_dis_cens_trend, "05_files/dp_dis_cens_trend.rds")
beepr::beep(8)
```

```{r}
dp_dis_cens_trend <- readRDS("05_files/dp_dis_cens_trend.rds")
dp_dis_cens_trend$plot_auto
```

### Moderation
#### TIpred Effects
```{r}
summary(dis_cens_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_dis_cens_trend <- ct_mod_grid(
  dis_cens_trend_fit,
  latentNames = c("dis", "dis_trend"),
  effects     = c("dis"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, 2, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_dis_cens_trend, "05_files/mod_dis_cens_trend.rds")
beepr::beep(8)
```
```{r}
mod_dis_cens_trend <- readRDS("05_files/mod_dis_cens_trend.rds")
```

##### ZDIS
```{r}
#| fig-width: 6
#| fig-height: 4
mod_dis_cens_trend <- readRDS("05_files/mod_dis_cens_trend.rds")
patchwork::wrap_plots(lapply(mod_dis_cens_trend$zdis, `[[`, "plot"), ncol = 1, guides = "collect")
```

## CENSOR-PSIT

### Model Specification
```{r}
dis_sit_trend_data <- p5_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_dis, esm24, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

dis_sit_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_dis", "esm24"),
  latentNames   = c("dis", "psit", "dis_trend", "psit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4, 0),                                  # censored, continuous
  censormin     = c(min(dis_sit_trend_data$esm_dis, na.rm = TRUE), -Inf), # floor of esm_dis
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (psit_dis = psit -> dis)
  DRIFT = matrix(c(
    "dis_dis"         , "psit_dis"        , 0                 , 0                 ,
    "dis_psit"        , "psit_psit"       , 0                 , 0                 ,
    0                 , 0                 , "drift_dis_trend" , 0                 ,
    0                 , 0                 , 0                 , "drift_psit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_dis"     , 0              , 0              , 0              ,
    "diff_dis_psit", "diff_psit"    , 0              , 0              ,
    0              , 0              , 0              , 0              ,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_dis"     , 0               , 0               , 0               ,
    "T0var_dis_psit", "T0var_psit"    , 0               , 0               ,
    0               , 0               , 0               , 0               ,
    0               , 0               , 0               , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_dis_trend", "T0m_psit_trend"),
  CINT    = c(0, 0, "cint_dis_trend", "cint_psit_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_dis", 0,
    0,          "mvar_psit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
dis_sit_trend_mod$pars$indvarying <- dis_sit_trend_mod$pars$param %in%
  c("T0m_dis_trend", "T0m_psit_trend", "cint_dis_trend", "cint_psit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
dis_sit_trend_mod$pars[, eff] <- FALSE
dis_sit_trend_mod$pars[dis_sit_trend_mod$pars$matrix == "DRIFT" &
               dis_sit_trend_mod$pars$param %in% c("dis_dis", "psit_dis", "dis_psit", "psit_psit"), eff] <- TRUE

dis_sit_trend_mod$pars[dis_sit_trend_mod$pars$indvarying | rowSums(dis_sit_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(dis_sit_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
dis_sit_trend_fit <- ctFit(
  datalong = dis_sit_trend_data,
  model    = dis_sit_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(dis_sit_trend_fit, "05_files/dis_sit_trend_fit.Rds")
beepr::beep(8)
```

```{r}
dis_sit_trend_fit <- readRDS("05_files/dis_sit_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
dis_sit_trend_fit <- ctGenerateFromFit(dis_sit_trend_fit, nsamples = 100)
pp_dis_sit_trend <- ctPostPredPlots(dis_sit_trend_fit)
saveRDS(pp_dis_sit_trend, "05_files/pp_dis_sit_trend.rds")
dis_sit_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_dis_sit_trend <- readRDS("05_files/pp_dis_sit_trend.rds")
pp_dis_sit_trend$Density
pp_dis_sit_trend$MeanTrajectory
pp_dis_sit_trend$LaggedCovariance_esm_dis
pp_dis_sit_trend$LaggedCovariance_esm24
pp_dis_sit_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(dis_sit_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_dis_sit_trend <- ct_dpars_plot(dis_sit_trend_fit,
  exclude  = c("dis_trend", "psit_trend"),   # dynamic processes only
  times    = seq(0, 4, 0.01),
  nsamples = 100)
saveRDS(dp_dis_sit_trend, "05_files/dp_dis_sit_trend.rds")
beepr::beep(8)
```

```{r}
dp_dis_sit_trend <- readRDS("05_files/dp_dis_sit_trend.rds")
dp_dis_sit_trend$plot_auto
dp_dis_sit_trend$plot_cross
dp_dis_sit_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(dis_sit_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_dis_sit_trend <- ct_mod_grid(
  dis_sit_trend_fit,
  latentNames = c("dis", "psit"),
  effects     = c("dis", "dis>psit"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, 5, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_dis_sit_trend, "05_files/mod_dis_sit_trend.rds")
beepr::beep(8)
```
```{r}
mod_dis_sit_trend <- readRDS("05_files/mod_dis_sit_trend.rds")
```

##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_dis_sit_trend <- readRDS("05_files/mod_dis_sit_trend.rds")
patchwork::wrap_plots(lapply(mod_dis_sit_trend$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```

## CENSOR-SSIT

### Model Specification
```{r}
dis_str_trend_data <- p5_data %>%
  group_by(id) %>%
  mutate(time_day = time_day + (ave(time_day, time_day, FUN = seq_along) - 1) / 1440) %>%
  ungroup() %>%
  arrange(id, time_day) %>%
  mutate(across(c(esm_dis, esm25, zpos, zneg, zdis), as.numeric)) %>%
  as.data.frame()

dis_str_trend_mod <- ctModel(
  type = "ct", id = "id", time = "time_day",
  manifestNames = c("esm_dis", "esm25"),
  latentNames   = c("dis", "ssit", "dis_trend", "ssit_trend"),
  TIpredNames   = c("zpos", "zneg", "zdis"),
  manifesttype  = c(4, 0),                                  # censored, continuous
  censormin     = c(min(dis_str_trend_data$esm_dis, na.rm = TRUE), -Inf), # floor of esm_dis
  censormax     = c(Inf, Inf),
  # each observed variable = dynamic process + trend factor
  LAMBDA = cbind(diag(2), diag(2)),
  # DRIFT -- labels are predictor_outcome (ssit_dis = ssit -> dis)
  DRIFT = matrix(c(
    "dis_dis"         , "ssit_dis"        , 0                 , 0                 ,
    "dis_ssit"        , "ssit_ssit"       , 0                 , 0                 ,
    0                 , 0                 , "drift_dis_trend" , 0                 ,
    0                 , 0                 , 0                 , "drift_ssit_trend"),
    4, 4, byrow = TRUE),
  # DIFFUSION -- system noise on the dynamic processes only
  DIFFUSION = matrix(c(
    "diff_dis"     , 0              , 0              , 0              ,
    "diff_dis_ssit", "diff_ssit"    , 0              , 0              ,
    0              , 0              , 0              , 0              ,
    0              , 0              , 0              , 0),
    4, 4, byrow = TRUE),
  # T0VAR -- first-beep deviations; trend starts come from random T0MEANS
  T0VAR = matrix(c(
    "T0var_dis"     , 0               , 0               , 0               ,
    "T0var_dis_ssit", "T0var_ssit"    , 0               , 0               ,
    0               , 0               , 0               , 0               ,
    0               , 0               , 0               , 0),
    4, 4, byrow = TRUE),
  T0MEANS = c(0, 0, "T0m_dis_trend", "T0m_ssit_trend"),
  CINT    = c(0, 0, "cint_dis_trend", "cint_ssit_trend"),
  MANIFESTMEANS = 0,
  MANIFESTVAR = matrix(c(
    "mvar_dis", 0,
    0,          "mvar_ssit"), 2, 2, byrow = TRUE)
)

# Random effects = the trend factors' T0MEANS and CINT only (EAS default)
dis_str_trend_mod$pars$indvarying <- dis_str_trend_mod$pars$param %in%
  c("T0m_dis_trend", "T0m_ssit_trend", "cint_dis_trend", "cint_ssit_trend")

# TIpreds moderate the four dynamic DRIFT cells (auto- and cross-effects) only
eff <- paste0(c("zpos", "zneg", "zdis"), "_effect")
dis_str_trend_mod$pars[, eff] <- FALSE
dis_str_trend_mod$pars[dis_str_trend_mod$pars$matrix == "DRIFT" &
               dis_str_trend_mod$pars$param %in% c("dis_dis", "ssit_dis", "dis_ssit", "ssit_ssit"), eff] <- TRUE

dis_str_trend_mod$pars[dis_str_trend_mod$pars$indvarying | rowSums(dis_str_trend_mod$pars[, eff]) > 0,
               c("matrix", "row", "col", "param", "indvarying", eff)]

ctModelLatexHTML(dis_str_trend_mod)
```

### Fit Model
```{r}
#| eval: false
ctJuliaSetup(threads = 10, force = TRUE)   # fresh engine (cached per model shape)
dis_str_trend_fit <- ctFit(
  datalong = dis_str_trend_data,
  model    = dis_str_trend_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(dis_str_trend_fit, "05_files/dis_str_trend_fit.Rds")
beepr::beep(8)
```

```{r}
dis_str_trend_fit <- readRDS("05_files/dis_str_trend_fit.Rds")
```

### Posterior Predictive Check
```{r}
#| eval: false
dis_str_trend_fit <- ctGenerateFromFit(dis_str_trend_fit, nsamples = 100)
pp_dis_str_trend <- ctPostPredPlots(dis_str_trend_fit)
saveRDS(pp_dis_str_trend, "05_files/pp_dis_str_trend.rds")
dis_str_trend_fit$generated <- NULL; gc()   # free memory
beepr::beep(8)
```

```{r}
pp_dis_str_trend <- readRDS("05_files/pp_dis_str_trend.rds")
pp_dis_str_trend$Density
pp_dis_str_trend$MeanTrajectory
pp_dis_str_trend$LaggedCovariance_esm_dis
pp_dis_str_trend$LaggedCovariance_esm25
pp_dis_str_trend$SubjectLogLik
```

### Results Table
```{r}
ct_sig_table(dis_str_trend_fit)
```

### Auto- and Cross-Effects
```{r}
#| eval: false
set.seed(1111)
dp_dis_str_trend <- ct_dpars_plot(dis_str_trend_fit,
  exclude  = c("dis_trend", "ssit_trend"),   # dynamic processes only
  times    = seq(0, 3, 0.01),
  nsamples = 100)
saveRDS(dp_dis_str_trend, "05_files/dp_dis_str_trend.rds")
beepr::beep(8)
```

```{r}
dp_dis_str_trend <- readRDS("05_files/dp_dis_str_trend.rds")
dp_dis_str_trend$plot_auto
dp_dis_str_trend$plot_cross
dp_dis_str_trend$peaks %>%
  dplyr::select(Effect, `Time interval`, median, lower, upper) %>%
  ct_sig_gt(lower = "lower", upper = "upper")
```

### Moderation
#### TIpred Effects
```{r}
summary(dis_str_trend_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  ct_sig_gt(lower = "2.5%", upper = "97.5%")
```

#### Moderation Plots
```{r}
#| eval: false
set.seed(1111)
mod_dis_str_trend <- ct_mod_grid(
  dis_str_trend_fit,
  latentNames = c("dis", "ssit"),
  effects     = c("dis", "dis>ssit"),
  tipreds     = c("zdis"),
  labels      = c(zdis = "Disorganized Schizotypy"),
  times       = seq(0, 3, 0.01),
  nsamp_use   = 100,
  x_lab       = "Time (days)"
)
saveRDS(mod_dis_str_trend, "05_files/mod_dis_str_trend.rds")
beepr::beep(8)
```
```{r}
mod_dis_str_trend <- readRDS("05_files/mod_dis_str_trend.rds")
```
##### ZDIS
```{r}
#| fig-width: 12
#| fig-height: 8
mod_dis_str_trend <- readRDS("05_files/mod_dis_str_trend.rds")
patchwork::wrap_plots(lapply(mod_dis_str_trend$zdis, `[[`, "plot"), ncol = 2, guides = "collect")
```
