---
title: "Disorganized Experiences"
format:
  html:
    toc: true
    toc-depth: 6
code-line-numbers: true
code-annotations: true
editor_options:
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/ct_halflife.R")
source("cust_funcs/mod_plot.R")
```

```{r}
#| include: false
p5_data <- readRDS("data/p2_data.Rds")
```

### Standardize Variables
```{r}
p5_data <- p5_data %>%
  mutate(across(c(esm_dis, esm_dis_con, zpos, zneg, zdis), scale))

p5_data %>%
  select(esm_dis, esm_dis_bin, esm_dis_con, zpos, zneg, zdis) %>%
  psych::describe()
```

### Julia Backend Setup
```{r}
ctJuliaSetup(threads = 10, force = TRUE)
```

## Two-Part Approach (Censored Magnitude)

### Model Specification
```{r}
dis_twopart_ctsem <- "
# Measurement Model
## BINARY
bin_dis_B =~ esm_dis_bin
bin_dis_W =~ esm_dis_bin

## CONT.
con_dis_B =~ esm_dis_con
con_dis_W =~ esm_dis_con

# Between
bin_dis_B  ~  0*bin_dis_B
bin_dis_B ~~  0*bin_dis_B
bin_dis_B %~% bin_dis_B

con_dis_B  ~  0*con_dis_B
con_dis_B ~~  0*con_dis_B
con_dis_B %~% con_dis_B

bin_dis_B %~% con_dis_B

# Within (dynamic) factor
## BINARY
bin_dis_W  ~  bin_dis_W
bin_dis_W ~~  bin_dis_W
bin_dis_W %~% bin_dis_W

## CONT.
con_dis_W  ~  con_dis_W
con_dis_W ~~  con_dis_W
con_dis_W %~% con_dis_W

## T0MEAN
bin_dis_B ~t0~ 1
con_dis_B ~t0~ 1

BINARY: esm_dis_bin
CENSOR: esm_dis_con
"

dis_twopart_syn <- ct_lavaan(dis_twopart_ctsem, data = p5_data)

dis_twopart_mod <- ctModel(
  type          = "ct",
  id            = "id",
  time          = "time_day",
  latentNames   = dis_twopart_syn$latentNames,
  manifestNames = dis_twopart_syn$manifestNames,
  LAMBDA        = dis_twopart_syn$LAMBDA,
  DRIFT         = dis_twopart_syn$DRIFT,
  DIFFUSION     = dis_twopart_syn$DIFFUSION,
  T0VAR         = dis_twopart_syn$T0VAR,
  CINT          = dis_twopart_syn$CINT,
  T0MEANS       = dis_twopart_syn$T0MEANS,
  MANIFESTMEANS = dis_twopart_syn$MANIFESTMEANS,
  manifesttype  = dis_twopart_syn$manifesttype,
  censormin     = dis_twopart_syn$censormin,
  censormax     = dis_twopart_syn$censormax,
  n.TIpred      = 3,
  TIpredNames   = c("zpos", "zneg", "zdis")
)

effect_cols <- c("zpos_effect", "zneg_effect", "zdis_effect")

# Only interested in cross-level moderation of the within-person (dynamic)
# processes' autoregression -- not the between-person/trait processes, and
# not any of the bin<->con cross-latent DRIFT paths (never specified in
# this spec, fixed at 0 by default, but ctModel() still defaults their
# TIpred effects to TRUE regardless of that fixed value). Start by
# switching every parameter's TIpred effects off, then re-enable only the
# two within-person autoregressions.
dis_twopart_mod$pars[, effect_cols] <- FALSE

bin_w_idx <- match("bin_dis_W", dis_twopart_syn$latentNames)
con_w_idx <- match("con_dis_W", dis_twopart_syn$latentNames)

target_bin_w <- dis_twopart_mod$pars$matrix == "DRIFT" &
  as.character(dis_twopart_mod$pars$row) == as.character(bin_w_idx) &
  as.character(dis_twopart_mod$pars$col) == as.character(bin_w_idx)
target_con_w <- dis_twopart_mod$pars$matrix == "DRIFT" &
  as.character(dis_twopart_mod$pars$row) == as.character(con_w_idx) &
  as.character(dis_twopart_mod$pars$col) == as.character(con_w_idx)

dis_twopart_mod$pars[target_bin_w | target_con_w, effect_cols] <- TRUE


stopifnot("indvarying" %in% names(dis_twopart_mod$pars))
dis_twopart_mod$pars[target_bin_w | target_con_w, "indvarying"] <- TRUE

print(dis_twopart_mod$pars[dis_twopart_mod$pars$matrix == "DRIFT",
                           c("matrix", "row", "col", "indvarying", effect_cols)])


ctModelLatexHTML(dis_twopart_mod)
```

### Fit Model
```{r}
#| eval: false
dis_twopart_fit <- ctFit(
  datalong = p5_data,
  model    = dis_twopart_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(dis_twopart_fit, "05_files/dis_twopart_fit.Rds")
```

### Evaluate Model Fit
```{r}
dis_twopart_fit <- readRDS("05_files/dis_twopart_fit.Rds")
summary(dis_twopart_fit)
ctModelLatexHTML(dis_twopart_fit)
```

#### Posterior Predictive Check
```{r}
#| eval: false
pp_plot_dis_twopart_fit <- ctPostPredPlots(dis_twopart_fit)
saveRDS(pp_plot_dis_twopart_fit, "05_files/pp_plot_dis_twopart_fit.Rds")
```

```{r}
pp_plot_dis_twopart_fit <- readRDS("05_files/pp_plot_dis_twopart_fit.Rds")

pp_plot_dis_twopart_fit$Density
pp_plot_dis_twopart_fit$MeanTrajectory
pp_plot_dis_twopart_fit$LaggedCovariance_esm_dis_bin
pp_plot_dis_twopart_fit$LaggedCovariance_esm_dis_con
pp_plot_dis_twopart_fit$SubjectLogLik
```

### Visual
```{r}
dis_twopart_halflife <- ct_halflife(dis_twopart_fit, dis_twopart_syn$latentNames)
dis_twopart_halflife %>% gt::gt()
```

:::callout-note
Half-life = time for a deviation from equilibrium to decay to half its size: `log(2) / -drift`, in days and hours (only defined when drift < 0). Occurrence (`bin_dis_W`) decays with a half-life of about `r round(dis_twopart_halflife$halflife_hours[dis_twopart_halflife$latent == "bin_dis_W"], 2)` hours, versus about `r round(dis_twopart_halflife$halflife_days[dis_twopart_halflife$latent == "con_dis_W"], 2)` days for magnitude (`con_dis_W`).
:::

#### Binary
```{r}
set.seed(1111)
ct_effects_plot(
  dis_twopart_fit,
  effects = c("bin_dis_W>bin_dis_W"),
  times = seq(0, 8, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Two-Part (Censored Magnitude)",
  legend_labels = c("DIS (occurrence) -> DIS (occurrence)"),
  latentNames = dis_twopart_syn$latentNames
)
```

#### Magnitude
```{r}
set.seed(1111)
ct_effects_plot(
  dis_twopart_fit,
  effects = c("con_dis_W>con_dis_W"),
  times = seq(0, 1, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Two-Part (Censored Magnitude)",
  legend_labels = c("DIS (magnitude) -> DIS (magnitude)"),
  latentNames = dis_twopart_syn$latentNames
)
```

### Binary Cross-level Interaction
#### Auto-Effect
```{r}
summary(dis_twopart_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("auto_bin_dis_W", param)) %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  gt::gt()
```

:::callout-note
No significant interactions.
:::

### Continuous Cross-level Interaction
#### Auto-Effect
```{r}
summary(dis_twopart_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("auto_con_dis_W", param)) %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  gt::gt()
```

:::callout-note
Two significant cross-level interactions. 
ZNEG is associated with faster decay, and ZDIS associated with slower decay.
:::

#### ZNEG
```{r}
#| eval: false
zneg_dis_con_cross <- plot_ribbon_multi(
  dis_twopart_fit,
  interaction  = "tip_zneg_auto_con_dis_W",
  times        = seq(0, 1, 0.05),
  nsamp_use    = 200,
  x_lab        = "Time (days)",
  legend_title = "Negative Schitzotypy",
  line_width   = 0.5,
  bound_width  = 0.3
)
saveRDS(zneg_dis_con_cross, "05_files/zneg_dis_con_cross.rds")
beepr::beep(8)
```

```{r}
zneg_dis_con_cross <- readRDS("05_files/zneg_dis_con_cross.rds")
zneg_dis_con_cross$plot
```

:::callout-note
Low Neg-Z demosntrates slower decay, while high Neg-Z demonstrates faster decay.
:::


#### ZDIS
```{r}
#| eval: false
zdis_dis_con_cross <- plot_ribbon_multi(
  dis_twopart_fit,
  interaction  = "tip_zdis_auto_con_dis_W",
  times        = seq(0, 1, 0.05),
  nsamp_use    = 200,
  x_lab        = "Time (days)",
  legend_title = "Disorganized Schitzotypy",
  line_width   = 0.5,
  bound_width  = 0.3
)
saveRDS(zdis_dis_con_cross, "05_files/zdis_dis_con_cross.rds")
beepr::beep(8)
```

```{r}
zdis_dis_con_cross <- readRDS("05_files/zdis_dis_con_cross.rds")
zdis_dis_con_cross$plot
```

:::callout-note
High Dis-Z demosntrates slower decay, while low Dis-Z demonstrates decay comparable to median Dis-Z.
:::
