---
title: "Negative Experiences"
format:
  html:
    toc: true
    toc-depth: 6
code-line-numbers: true
code-annotations: true
editor_options:
  chunk_output_type: console
execute:
  warning: FALSE
---

## Initial Set Up
### Load Packages/Cust Functions
```{r}
pacman::p_load(tidyverse, ctsem)
source("cust_funcs/lavaan_parser.R")
source("cust_funcs/ct_plot.R")
source("cust_funcs/ct_latex_html.R")
source("cust_funcs/mod_plot.R")
```

```{r}
#| include: false
p6_data <- readRDS("data/p2_data.Rds")
```

### Standardize Variables
```{r}
p6_data <- p6_data %>%
  mutate(across(c(esm_neg3, esm_neg3_con, zpos, zneg, zdis), scale))

p6_data %>%
  select(esm_neg3, esm_neg3_bin, esm_neg3_con, zpos, zneg, zdis) %>%
  psych::describe()
```

### Julia Backend Setup
```{r}
ctJuliaSetup(threads = 10, force = TRUE)
```

## Two-Part Approach (Censored Magnitude)

### Model Specification
```{r}
neg3_twopart_ctsem <- "
# Measurement Model
## BINARY
bin_neg3_B =~ esm_neg3_bin
bin_neg3_W =~ esm_neg3_bin

## CONT.
con_neg3_B =~ esm_neg3_con
con_neg3_W =~ esm_neg3_con

# Between/Trend
bin_neg3_B  ~  0*bin_neg3_B
bin_neg3_B ~~  0*bin_neg3_B
bin_neg3_B %~% bin_neg3_B

con_neg3_B  ~  0*con_neg3_B
con_neg3_B ~~  0*con_neg3_B
con_neg3_B %~% con_neg3_B

bin_neg3_B %~% con_neg3_B

# Within (dynamic) factor
## BINARY
bin_neg3_W  ~  bin_neg3_W
bin_neg3_W ~~  bin_neg3_W
bin_neg3_W %~% bin_neg3_W

## CONT.
con_neg3_W  ~  con_neg3_W
con_neg3_W ~~  con_neg3_W
con_neg3_W %~% con_neg3_W

## T0MEAN
bin_neg3_B ~t0~ 1
con_neg3_B ~t0~ 1

BINARY: esm_neg3_bin
CENSOR: esm_neg3_con
"

neg3_twopart_syn <- ct_lavaan(neg3_twopart_ctsem, data = p6_data)

neg3_twopart_mod <- ctModel(
  type          = "ct",
  id            = "id",
  time          = "time_day",
  latentNames   = neg3_twopart_syn$latentNames,
  manifestNames = neg3_twopart_syn$manifestNames,
  LAMBDA        = neg3_twopart_syn$LAMBDA,
  DRIFT         = neg3_twopart_syn$DRIFT,
  DIFFUSION     = neg3_twopart_syn$DIFFUSION,
  T0VAR         = neg3_twopart_syn$T0VAR,
  CINT          = neg3_twopart_syn$CINT,
  T0MEANS       = neg3_twopart_syn$T0MEANS,
  MANIFESTMEANS = neg3_twopart_syn$MANIFESTMEANS,
  manifesttype  = neg3_twopart_syn$manifesttype,
  censormin     = neg3_twopart_syn$censormin,
  censormax     = neg3_twopart_syn$censormax,
  n.TIpred      = 3,
  TIpredNames   = c("zpos", "zneg", "zdis")
)

effect_cols <- c("zpos_effect", "zneg_effect", "zdis_effect")

# Only interested in cross-level moderation of the within-person (dynamic)
# processes' autoregression -- not the between-person/trait processes, and
# not any of the bin<->con cross-latent DRIFT paths (never specified in
# this spec, fixed at 0 by default, but ctModel() still defaults their
# TIpred effects to TRUE regardless of that fixed value). Start by
# switching every parameter's TIpred effects off, then re-enable only the
# two within-person autoregressions.
neg3_twopart_mod$pars[, effect_cols] <- FALSE

bin_w_idx <- match("bin_neg3_W", neg3_twopart_syn$latentNames)
con_w_idx <- match("con_neg3_W", neg3_twopart_syn$latentNames)

target_bin_w <- neg3_twopart_mod$pars$matrix == "DRIFT" &
  as.character(neg3_twopart_mod$pars$row) == as.character(bin_w_idx) &
  as.character(neg3_twopart_mod$pars$col) == as.character(bin_w_idx)
target_con_w <- neg3_twopart_mod$pars$matrix == "DRIFT" &
  as.character(neg3_twopart_mod$pars$row) == as.character(con_w_idx) &
  as.character(neg3_twopart_mod$pars$col) == as.character(con_w_idx)

neg3_twopart_mod$pars[target_bin_w | target_con_w, effect_cols] <- TRUE

# Safety check: ctModel() has been observed to silently default
# indvarying = FALSE on a free DRIFT diagonal parameter (found with
# con_psx_W in 03_ple_model.qmd) even when nothing in this script asked
# for that. Confirm both within-person autoregressions are still
# individually varying, and force them back on if ctModel() defaulted
# either off.
stopifnot("indvarying" %in% names(neg3_twopart_mod$pars))
neg3_twopart_mod$pars[target_bin_w | target_con_w, "indvarying"] <- TRUE

print(neg3_twopart_mod$pars[neg3_twopart_mod$pars$matrix == "DRIFT",
                           c("matrix", "row", "col", "indvarying", effect_cols)])

ctModelLatexHTML(neg3_twopart_mod)
```

### Fit Model
```{r}
#| eval: false
neg3_twopart_fit <- ctFit(
  datalong = p6_data,
  model    = neg3_twopart_mod,
  backend  = "julia",
  optimcontrol = list(maxiter = 10000),
  cores = 10, plot = FALSE, priors = TRUE
)
saveRDS(neg3_twopart_fit, "06_files/neg3_twopart_fit.Rds")
```

### Evaluate Model Fit
```{r}
neg3_twopart_fit <- readRDS("06_files/neg3_twopart_fit.Rds")
summary(neg3_twopart_fit)
ctModelLatexHTML(neg3_twopart_fit)
```

#### Posterior Predictive Check
```{r}
#| eval: false
pp_plot_neg3_twopart_fit <- ctPostPredPlots(neg3_twopart_fit)
saveRDS(pp_plot_neg3_twopart_fit, "06_files/pp_plot_neg3_twopart_fit.Rds")
```

```{r}
pp_plot_neg3_twopart_fit <- readRDS("06_files/pp_plot_neg3_twopart_fit.Rds")

pp_plot_neg3_twopart_fit$Density
pp_plot_neg3_twopart_fit$MeanTrajectory
pp_plot_neg3_twopart_fit$LaggedCovariance_esm_neg3_bin
pp_plot_neg3_twopart_fit$LaggedCovariance_esm_neg3_bin
pp_plot_neg3_twopart_fit$SubjectLogLik
```

### Visual
#### Binary
```{r}
set.seed(1111)
ct_effects_plot(
  neg3_twopart_fit,
  effects = c("bin_neg3_W>bin_neg3_W"),
  times = seq(0, 8, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Two-Part (Censored Magnitude)",
  legend_labels = c("Neg Exp. (occurrence) -> Neg Exp. (occurrence)"),
  latentNames = neg3_twopart_syn$latentNames
)
```

#### Magnitude
```{r}
set.seed(1111)
ct_effects_plot(
  neg3_twopart_fit,
  effects = c("con_neg3_W>con_neg3_W"),
  times = seq(0, 3, 0.01),
  ylim = c(0, 1),
  title = "Auto-effects: Two-Part (Censored Magnitude)",
  legend_labels = c("Neg Exp. (magnitude) -> Neg Exp. (magnitude)"),
  latentNames = neg3_twopart_syn$latentNames
)
```

### Binary Cross-level Interaction
#### Auto-Effect
```{r}
summary(neg3_twopart_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("auto_bin_neg3_W", param)) %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  gt::gt()
```

:::callout-note
No significant cross-level interactions.
:::

### Continuous Cross-level Interaction
#### Auto-Effect
```{r}
summary(neg3_twopart_fit)$tipreds %>%
  as.data.frame() %>%
  tibble::rownames_to_column("param") %>%
  filter(grepl("auto_con_neg3_W", param)) %>%
  select(param, mean, `2.5%`, `97.5%`) %>%
  gt::gt()
```

:::callout-note
One significant cross-level interaction. 
ZDIS is associated with slower decay.
:::

#### ZDIS
```{r}
#| eval: false
zdis_neg3_con_cross <- plot_ribbon_multi(
  neg3_twopart_fit,
  interaction  = "tip_zdis_auto_con_neg3_W",
  times        = seq(0, 4, 0.05),
  nsamp_use    = 200,
  x_lab        = "Time (days)",
  legend_title = "Disorganized Schitzotypy",
  line_width   = 0.5,
  bound_width  = 0.3
)
saveRDS(zdis_neg3_con_cross, "06_files/zdis_neg3_con_cross.rds")
beepr::beep(8)
```

```{r}
zdis_neg3_con_cross <- readRDS("06_files/zdis_neg3_con_cross.rds")
zdis_neg3_con_cross$plot
```

:::callout-note
High Dis-Z demosntrates slower decay, while low Dis-Z demonstrates decay comparable to median Dis-Z.
:::
